---
title: "RecursionAnalysis"
author: "Junyi Chu, Rose M. Schneider, Pierina Cheung"
date: "7/19/2018"
output: 
  html_document:
    toc: yes
    toc_float: yes
---

# Setup
```{r setup, include=FALSE}
rm(list = ls())
require("knitr")
# opts_knit$set(root.dir = "~/Documents/Projects/recursion/") #this is specific to RMS, change accordinglyz
#opts_knit$set(root.dir = "~/Sites/jchu.github.io/recursion/")
#opts_knit$set(root.dir = "/Users/MotherTao/Documents/junyidata/recursion")
opts_knit$set(root.dir = "~/Projects/Junyi study/recursiongithub") #Pierina's PC computer
library(tidyverse)
library(magrittr)
#library(langcog)
library(lme4)
library(stringr)
library(RColorBrewer)
library(ggthemes)
```

## Loading data
```{r}
#original data
full.data <- read.csv('data/recursion_full.csv', na.strings=c(""," ","NA", "NA "))
```

Reasons for exclusion and their numbers
```{r}
full.data %>%
  dplyr::filter(ExclusionGroup != "include") %>%
  dplyr::distinct(LadlabID, .keep_all = TRUE) %>%
  dplyr::group_by(ExclusionGroup) %>%
  dplyr::summarize(countN = dplyr::n_distinct(LadlabID)) %>%
  kable()
```

First, let's remove anyone who should not be included in the final dataset.
```{r}
full.data %<>%
  dplyr::filter(ExclusionGroup == "include")
```

Now, add in the Productivity classification, IHC, and FHC from PC, JC, and RMS coding

<span style="color:red">Question from RMS: is FHC capped at 100 as well?</span>

```{r}
#productivity, fhc, ihc coding from pc, jc, and rms
hc.data <- read.csv('data/HC-datawide-forcoding - hc.datawide.csv') %>%
  dplyr::select(LadlabID, prod_tomerge, ihc_tomerge, fhc_tomerge, dce)

full.data <- dplyr::right_join(full.data, hc.data, by = "LadlabID")

full.data %<>%
  dplyr::rename(Productivity = prod_tomerge, 
                IHC = ihc_tomerge, 
                FHC = fhc_tomerge, 
                DCE = dce)%>%
  dplyr::mutate(Productivity = factor(Productivity, levels = c("nonprod", "prod"), 
                               labels = c("Nonproductive", "Productive")), 
         IHC = ifelse(IHC > 100, 100, IHC),
         FHC = ifelse(FHC > 100, 100, FHC))
```

Number of kids by age group and average age
```{r}
full.data %>%
  dplyr::group_by(AgeGroup) %>%
  dplyr::summarize(sumAge = n_distinct(LadlabID)) %>%
  kable()

full.data %>%
  dplyr::distinct(LadlabID, .keep_all = TRUE) %>%
  dplyr::summarize(minAge = min(Age),
            maxAge = max(Age),
            meanAge = mean(Age),
            sdAge = sd(Age)) %>%
  kable()
```

Number of kids who were classified as prod, nonprod, NA
```{r}
full.data %>%
  dplyr::distinct(LadlabID, Productivity)%>%
  dplyr::group_by(Productivity)%>%
  dplyr::summarise(n = n()) %>%
  kable()
```

Just for reference, this is the number of kids who switched classifications from PC, JC, RMS recode
```{r}
full.data %>%
  dplyr::filter(TaskType == "productivity") %>%
  #droplevels()%>%
  dplyr::distinct(LadlabID, Response, Productivity) %>%
  dplyr::mutate(Response = factor(Response, levels = c("nonprod", "prod"), 
                           labels = c("Nonproductive", "Productive")))%>%
  dplyr::mutate(changed_classification = ifelse((is.na(Response) & Productivity == "Nonproductive"),
                                         "NA_toNonprod",
                                         ifelse((is.na(Response) & Productivity == "Productive"), 
                                                "NA_toProd", 
                                                ifelse((Response == "Nonproductive" & Productivity == "Productive"), 
                                                       "Nonprod_toProd", 
                                                       ifelse((Response == "Productive" & Productivity == "Nonproductive"),
                                                              "Prod_toNonprod", "no_change")))))%>%
  dplyr::group_by(changed_classification)%>%
  dplyr::summarise(n =n())
```

***
# Highest Count Descriptives
Average of IHC, DCE, and FHC for all kids
```{r}
full.data %>%
  dplyr::distinct(LadlabID, IHC, FHC, DCE)%>%
  dplyr::summarise(mean_IHC = mean(IHC),
            sd_IHC = sd(IHC),
            mean_FHC = mean(FHC),
            sd_FHC = sd(FHC), 
            mean_DCE = mean(DCE, na.rm = TRUE), 
            sd_DCE = sd(DCE, na.rm = TRUE)) %>%
  kable()
```

Same data by productivity
```{r}
full.data %>%
  dplyr::distinct(LadlabID, Productivity, FHC, IHC, DCE)%>%
  dplyr::group_by(Productivity)%>%
  dplyr::summarise(mean_IHC = mean(IHC),
            sd_IHC = sd(IHC),
            mean_FHC = mean(FHC),
            sd_FHC = sd(FHC), 
            mean_DCE = mean(DCE, na.rm = TRUE), 
            sd_DCE = sd(DCE, na.rm = TRUE)) %>%
  kable()
```

Plotting distribution of IHC, as a function of productivity (~ junyi's graph)

```{r}
unique.hc.data <- full.data %>%
  dplyr::distinct(LadlabID, Gender, Age, AgeGroup, HCReceivedSupport, IHC, DCE, FHC, Productivity)

ggplot(unique.hc.data, aes(x=IHC, color=Productivity)) + 
  geom_dotplot(aes(fill = Productivity),
    binwidth=1, stackgroups=TRUE, binpositions="all",method="dotdensity") +
  scale_color_brewer(palette="Set2") + 
  scale_fill_brewer(palette="Set2") +
  coord_fixed(ratio=1) +
  scale_y_continuous(breaks=seq(0,40,10), lim=c(0,35)) +
  scale_x_continuous(breaks=seq(0,100,by=10)) +
  labs(title="Initial Highest Count",  
       x="IHC (no error)", 
       y="Frequency") +
  theme_bw() + 
  theme(legend.position="bottom")

# hist(unique.hc.data$IHC)
```

Plotting productivity as a function of age in months

```{r}
unique.hc.data$AgeMonths = floor(unique.hc.data$Age*12)

ggplot(unique.hc.data, aes(x=AgeMonths, colour = Productivity)) + 
  geom_dotplot(aes(fill = Productivity),
               binwidth = 1,
               stackgroups=TRUE, binpositions="all") +
  coord_fixed(ratio=1) +
  scale_y_continuous(breaks=seq(0,10,5), lim=c(0,12)) +
  scale_x_continuous(breaks=seq(48,72,by=6)) +
  scale_color_brewer(palette="Set2") + 
  scale_fill_brewer(palette="Set2") +
  labs(title="Productivity by Age", 
       x="Age in Months", 
       y="Frequency") +
  theme_bw() + 
  theme(legend.position="bottom")
```

## Distance between IHC and FHC

Restruture data to plot distance between ihc, dce, and final count
```{r}
hc.dev.data <- full.data %>%
  dplyr::select(LadlabID, Age, Productivity, IHC, DCE, FHC) %>%
  gather(hcprogression, hc, IHC:FHC)%>%
  mutate(hcprogression = factor(hcprogression, levels = c("IHC", "DCE", "FHC")))

#all kids together
ggplot(hc.dev.data, aes(x = LadlabID, y = hc)) + 
  facet_grid(rows = vars(Productivity)) +
  geom_line() + 
  geom_point(aes(shape = hcprogression, colour = hcprogression), 
             size = 2, stroke = 1.5) +
  scale_color_brewer(palette="Dark2") +
  scale_shape_manual(values = c(4,5,20)) +
  labs(title="Highest Count Progression by Decade Productivity",
       x = "Each line = individual kids",
       y="Highest Count by Count Type") +
  theme_bw() + 
  theme(legend.position="bottom", 
        axis.text.x = element_text(angle = 270, hjust = 1))

#for easier viewing, just going to break this up into individual plots
#productive
ggplot(subset(hc.dev.data, Productivity == "Productive"), aes(x = LadlabID, y = hc)) + 
  facet_grid(rows = vars(Productivity)) +
  geom_line() + 
  geom_point(aes(shape = hcprogression, colour = hcprogression), 
             size = 2, stroke = 1.5) +
  scale_color_brewer(palette="Dark2") +
  scale_shape_manual(values = c(4,5,20)) +
  labs(title="Highest Count Progression by Decade Productivity",
       x = "Each line = individual kids",
       y="Highest Count by Count Type") +
  theme_bw() + 
  theme(legend.position="bottom", 
        axis.text.x = element_text(angle = 270, hjust = 1)) + 
  labs(title = "Distance, Productive")

#nonproductive
ggplot(subset(hc.dev.data, Productivity == "Nonproductive"), aes(x = LadlabID, y = hc)) + 
  facet_grid(rows = vars(Productivity)) +
  geom_line() + 
  geom_point(aes(shape = hcprogression, colour = hcprogression), 
             size = 2, stroke = 1.5) +
  scale_color_brewer(palette="Dark2") +
  scale_shape_manual(values = c(4,5,20)) +
  labs(title="Highest Count Progression by Decade Productivity",
       x = "Each line = individual kids",
       y="Highest Count by Count Type") +
  theme_bw() + 
  theme(legend.position="bottom", 
        axis.text.x = element_text(angle = 270, hjust = 1)) + 
  labs(title = "Distance, Nonproductive")
```

Average number of decade prompts provided. M = 3.3 (SD = 1.7), range 1 to 7, N = 38. 42 kids counted to 99 on their own
```{r}
full.data %>%
  filter(TaskItem == "times") %>%
  filter(Productivity == "Productive") %>%
  distinct(LadlabID, HCReceivedSupport, TaskItem, Response) %>%
  mutate(Response = as.numeric(levels(Response)[Response])) %>%
  group_by(HCReceivedSupport) %>%
  summarize(mean = mean(Response, na.rm=TRUE),
            sd = sd(Response, na.rm=TRUE),
            min = min(Response, na.rm=TRUE),
            max = max(Response, na.rm=TRUE),
            count=n())
# assume 0 = NA
# error in supported.times coding, should only count to 90
# but one kid got prompted with 100 and 110 and times should be 0
```


# What Comes Next Descriptives

First check if Accuracy column in full.data is coded correctly. Good to go.
```{r}
wcn.data <- full.data %>%
   filter(Task == "WCN")

wcn.data %<>%
  mutate(Response_num = as.numeric(as.character(Response)), 
         TaskItem_num = as.numeric(as.character(TaskItem)), 
         Accuracy_check = ifelse(Response_num == (TaskItem_num + 1), 1, 0), 
         Accuracy_valid = ifelse(Accuracy == Accuracy_check, TRUE, FALSE))

validate <- function(){
  validation <- wcn.data %>%
  filter(Accuracy_valid == FALSE)
  if(length(validation$LadlabID) > 0) {
    print("WARNING: CHECK CODING")
  } else {
    print("All coding correct")
  }
}

validate()
```


```{r}
# PC ask: do we need this?

# wcn.test <- wcn.data %>%
#  mutate(Response_num = as.numeric(as.character(Response)), 
#         TaskItem_num = as.numeric(as.character(TaskItem)), 
#         Response_check = ifelse(Response == Response_num, TRUE, FALSE), 
#         TaskItem_check = ifelse(TaskItem == TaskItem_num, TRUE, FALSE))%>%
#  filter(Response_check == FALSE | TaskItem_check == FALSE)
```

WCN: Children were provided with momentum trials if they got wrong on immediate trials. Check %trials where immediate = wrong, momentum = right
```{r}
wcn.wide <- full.data %>%
  filter(ExclusionGroup == "include") %>%
  filter(Task == "WCN") %>%
  filter(TaskType != "practice") %>%
  filter(TaskItem != 3) %>% # a trial on 3 for momentum that doesn't exist for immediate
  droplevels()%>%
  dplyr::select(LadlabID, Age, AgeGroup, TaskType, TaskItem, Accuracy, Productivity) %>%
  spread(TaskType, Accuracy)

# data check: there shouldn't be any kids who got 1 for immediate but 0 for momentum or 1 for immediate and 1 for momentum (less of a problem)
##pulling out these kids below
wcn.check <- full.data %>%
  filter(Task == "WCN", 
         TaskType == "momentum" | TaskType == "immediate")%>%
  dplyr::select(LadlabID, Age, AgeGroup, TaskType, TaskItem, Accuracy) %>%
  spread(TaskType, Accuracy)%>%
  mutate(issue_immediate1Momentum0 = ifelse(immediate == 1 & momentum == 0, TRUE, FALSE), 
         issue_immediate1Momentum1 = ifelse(immediate == 1 & momentum == 1, TRUE, FALSE))%>%
  filter(issue_immediate1Momentum0 == TRUE | 
           issue_immediate1Momentum1 == TRUE)
#7 kids with this issue - exclude??
#PC: I think we can keep them but we should check the coding sheet. Can keep because presumaly they shouldn't be tested on momentum if they got immeidate right.

# how many kids show improved performance
xtabs(~immediate + momentum, data = wcn.wide, na.action = na.pass, exclude = NULL)
# answer: 191 / 1048 trials = ~ 18%
```

Percent Correct on WCN
```{r}
wcn.wide %>%
  group_by(LadlabID) %>%
  summarize(avg.wcn = mean(immediate, na.rm=TRUE),
            sd.wcn = sd(immediate, na.rm=TRUE)) %>%
  summarize(avg = mean(avg.wcn),
            sd = sd(sd.wcn))

wcn.wide %>%
  group_by(LadlabID, Productivity) %>%
  summarize(avg.wcn = mean(immediate, na.rm=TRUE),
            sd.wcn = sd(immediate, na.rm=TRUE)) %>%
  group_by(Productivity) %>%
  summarize(avg = mean(avg.wcn),
            sd = sd(sd.wcn))
```
Plotting %corr on WCN as function of productivity
```{r}
wcn.wide %>%
  group_by(LadlabID, Productivity) %>%
  summarize(avg.wcn = mean(immediate, na.rm=TRUE),
            sd.wcn = sd(immediate, na.rm=TRUE)) %>%
  ggplot(aes(x = Productivity, y = avg.wcn, fill=factor(Productivity))) +
  stat_summary(fun.y = mean, position = position_dodge(width = .95), 
                      geom="bar", alpha = .5, colour = "black") +
  stat_summary(fun.data = mean_se, geom="errorbar", 
               position = position_dodge(width=0.90), width = 0.2)+
  scale_fill_discrete(name = "Decade Productivity") +
  ylab("Proportion Correct") + 
  xlab('') + 
  theme_bw() + 
  theme(legend.position = "none") +
  ggtitle("Overall proportion correct on the What Comes Next Task") +
  theme(text = element_text(size = 12)) +
  ylim(0, 1.0) +
  geom_violin(alpha = .1)
```
     
Add whether the Task Item was within or outside of the kid's initial highest count.
```{r}
#first, get initial highest count for each kiddo
#Make a lookup table with SID and initial highest count
lookup <- full.data %>%
  distinct(LadlabID, IHC)

wcn.wide %<>%
  mutate(TaskItem = as.numeric(as.character(TaskItem)))

#This is a function that, for each trial, checks the number queried. If number queried is above the child's initial highest count, marks that trial as beyond count range.
determine_count_range <- function(df) {
  tmp <- df
  for (row in 1:nrow(tmp)) {
    sub = as.character(tmp[row, "LadlabID"])
    count_range = as.numeric(as.character(subset(lookup, LadlabID == sub)$IHC))
    tmp[row, "IHC"] = as.numeric(as.character(count_range))
    if (tmp[row, "TaskItem"] > count_range) {
      tmp[row, "WithinOutsideIHC"] = "outside"
    } else {
      tmp[row, "WithinOutsideIHC"] = "within"
    }
  }
  return(tmp)
}

#Run for wcn
wcn.wide <- determine_count_range(wcn.wide)
```

WCN accuracy, within and outside of IHC
```{r}
wcn.wide %>%
  group_by(WithinOutsideIHC) %>%
  summarize(mean = mean(immediate, na.rm = TRUE), 
            sd = sd(immediate, na.rm = TRUE))
```
     

Now WCN by within/outside count range and productivity
```{r}
wcn.wide %>%
  group_by(Productivity, WithinOutsideIHC) %>%
  summarize(mean = mean(immediate, na.rm = TRUE), 
            sd = sd(immediate, na.rm = TRUE))
```

Plotting WCN as within vs. beyond by productivity 
<span style="color:red"> error bars don't work?! PC
```{r}
wcn.wide %>%
  group_by(Productivity, WithinOutsideIHC) %>%
  summarize(mean = mean(immediate, na.rm = TRUE), 
            sd = sd(immediate, na.rm = TRUE)) %>%
  ggplot(aes(x=Productivity, y=mean, fill=WithinOutsideIHC)) +
  stat_summary(fun.y = mean, position = position_dodge(width = .95), 
                      geom="bar", alpha = .5, colour = "black") +
  stat_summary(fun.data = mean_se, geom="errorbar", 
               position = position_dodge(width=0.90), width = 0.2) +
  scale_fill_discrete(name = "Within vs. Beyond IHC") +
  scale_y_continuous(lim=c(0,1)) +
  labs(title="Within vs. Beyond WCN by Productivity", 
       y="Proportion Correct", 
       fill="Item type") +
  theme_bw() +
  theme(text = element_text(size = 12))
```

How many trials do kids have beyond their IHC?
```{r}
wcn.wide %>%
 dplyr:: select(-momentum)%>%
  group_by(Productivity, WithinOutsideIHC)%>%
  summarise(n = n())
```

Highest contiguous NN

<span style="color:red">Note from RMS: There are a few kids that did not pass 1 or both of the practice trials for WCN. Are they to be included?</span>
```{r, warning = FALSE}
unique.nn <- as.vector(unique(wcn.wide$LadlabID))
#get the task items from wcn
nextnums <- as.vector(unique(wcn.wide$TaskItem))

##Okay so it looks like there are 16 participants who did not pass both practice trials for WCN. I may need to hardcode their Highest contiguous, but to be continued
x <- full.data %>%
  filter(Task == "WCN" &
           (TaskItem == 1 | TaskItem == 5))%>%
  group_by(LadlabID)%>%
  summarise(sum = sum(Accuracy))%>%
  filter(sum != 2)

#just hardcoding kids because it's easier than going back to the full data frame
#These kids got 1 right, 5 wrong: 
one.corr <- as.vector(c("012316-BO", "022616-JM", "030216-ED", 
              "030817-ZI", "031516-A", "032216-JH", 
              "032216-RC", "040317-AL", "040317-SL", 
              "041316-AR", "041316-NC", "041316-VN", 
              "062416-MC"))

five.corr <- as.vector("050617-Z1")

zero.corr <- as.vector(c("030216-AD", "040616-K"))
#this is a function that pulls out the largest number for which a participant had a correct consecutive
get_contiguous <- function(){
  contig <- data.frame()
  for (sub in unique.nn) {
    tmp <- wcn.wide %>%
      dplyr::select(LadlabID, Age, AgeGroup, TaskItem, immediate)%>%
      filter(LadlabID == sub, 
             immediate == 0)%>%
      mutate(TaskItem = sort(TaskItem))
    if (length(tmp$LadlabID) == 0) {
      highest_contig = 86
      sub_contig <- data.frame(sub, highest_contig)
      contig <- bind_rows(contig, sub_contig)
    } else if (length(tmp$TaskItem) > 0 & min(tmp$TaskItem) == 23) {
      if(sub %in% one.corr){
        highest_contig = 1
        sub_contig <- data.frame(sub, highest_contig)
        contig <- bind_rows(contig, sub_contig)
      } else if(sub %in% five.corr | sub %in% zero.corr){
        highest_contig = 0
        sub_contig <- data.frame(sub, highest_contig)
        contig <- bind_rows(contig, sub_contig)
      } else {
        highest_contig = 5
        sub_contig <- data.frame(sub, highest_contig)
        contig <- bind_rows(contig, sub_contig)
      }
    } else {
      min.nn <- min(tmp$TaskItem)
      prev_correct <- nextnums[nextnums < min.nn]
      highest_contig <- max(prev_correct)
    
      sub_contig <- data.frame(sub,
                             highest_contig)
      contig <- bind_rows(contig, sub_contig)
    }
  }
  return(contig)
}

highest_contiguous_nn <- get_contiguous()%>%
  dplyr::rename(LadlabID = sub)%>%
  distinct(LadlabID, highest_contig)%>%
  rename(Highest_Contig_NN = highest_contig)

```

Plotting freq of highest contiguous as a function of productivity
``` {r}
full.data %>%
  right_join(highest_contiguous_nn) %>%
  distinct(LadlabID, Highest_Contig_NN, Productivity) %>%
  ggplot(aes(x=Highest_Contig_NN, color=Productivity)) + 
  geom_dotplot(aes(fill = Productivity),
    binwidth=1, stackgroups=TRUE, binpositions="all",method="dotdensity") +
  scale_color_brewer(palette="Set2") + 
  scale_fill_brewer(palette="Set2") +
  coord_fixed(ratio=1) +
  scale_y_continuous(breaks=seq(0,50,10), lim=c(0,50)) +
  #scale_x_continuous(breaks=seq(0,100,by=10)) +
  scale_x_continuous(breaks = c(0, 1, 5, 23, 29, 37, 40, 62, 70, 86),
                     labels=c("0", "1", "5", "23", "29", "37", "40", "62", "70", "86")) +
  labs(title="Highest Contiguous Next Number by Decade Productivity",  
       x="Highest Contiguous Next Number", 
       y="Frequency") +
  theme_bw() + 
  theme(legend.position="bottom")

```

Check kids who didn't get both practice trials right on WCN
```{r}
wcn.prac.chk <- full.data %>%
  filter(LadlabID == "012316-BO" |LadlabID == "022616-JM"|LadlabID == "030216-ED"|
           LadlabID == "030817-ZI"|LadlabID == "031516-A"|LadlabID == "032216-JH"|
           LadlabID == "032216-RC"|LadlabID == "040317-AL"|LadlabID == "040317-SL"|
           LadlabID == "041316-AR"|LadlabID == "041316-NC"|LadlabID == "041316-VN"| 
           LadlabID == "062416-MC"|LadlabID == "050617-Z1" |LadlabID == "030216-AD"|
           LadlabID == "040616-K") %>%
  select(LadlabID, Age, AudioRecorded,Task, TaskType, TaskItem,Response, Accuracy, Productivity) %>%
  filter(Task == "WCN")

wcn.prac.chk %>%
  distinct(LadlabID, Productivity) %>%
  group_by(Productivity) %>%
  summarize(count=n())

wcn.prac.chk %>%
  distinct(LadlabID, AudioRecorded) %>%
  group_by(AudioRecorded) %>%
  summarize(count=n()) # 2 kids no audio

# who has audio?
wcn.prac.chk %>%
  distinct(LadlabID, AudioRecorded) %>%
  filter(AudioRecorded == "yes")

# PC checked audio for the following kids. cannot find a few where audiorecorded = yes. 
# Outcome: some clear include cases. but also a few where kids only passed momentum for "five", immeidate 5 not asked for #a second time. 
# I'm more inclined to include kids who passed 1outof2 prac trials bc that suggests kid #understood task?

# 1  022616-JM           yes
# 2  030216-AD           yes - fail both; exclude
# 3  030216-ED           yes - pass second time on immediate 5; include
# 4  030817-ZI           yes - pass both on first try; include
# 5   031516-A           yes
# 6  032216-JH           yes - pass 1 immediate & 5 momentum; include?
# 7  040317-AL           yes - pass second time on 5 immediate; include
# 8  040317-SL           yes - pass second time on 5 immediate; include
# 9   040616-K           yes - pass second time on 1 immediate, 5 momentum, and 3 immediate; include?
# 10 041316-AR           yes 
# 11 041316-NC           yes - pass 1 immediate, fail on 5 momentum; include?
# 12 041316-VN           yes
# 13 050617-Z1           yes
# 14 062416-MC           yes - pass second time on 5 immediate; include

```


# Infinity Descriptives
```{r}
full.data %>%
  dplyr::distinct(LadlabID, Category)%>%
  dplyr::group_by(Category)%>%
  dplyr::summarise(n = n())

full.data %>%
  dplyr::distinct(LadlabID, SuccessorKnower, Productivity)%>%
  dplyr::group_by(SuccessorKnower, Productivity)%>%
  dplyr::summarise(n = n()) %>%
  spread(Productivity, n)

full.data %>%
  dplyr::distinct(LadlabID, EndlessKnower, Productivity)%>%
  dplyr::group_by(EndlessKnower, Productivity)%>%
  dplyr::summarise(n = n()) %>%
  spread(Productivity, n)

````



# Analyses
## 1: Counting, Productivity, and Infinity Battery
To identify whether there is connection between counting experience and Infinity Task performance, we will conduct three initial analyses, predicting Infinity Task performance from either (1) Initial Highest Count, (2) Productivity for Decade Rule (defined above), or (3) performance on the Next Number task. 

glmer(inf.0/1 ~ (predictor) + age + (1|subject), family = binomial).

---
First, we need to make a model data frame that readily has all of this information

```{r}
#model base
model.df <- full.data %>%
  dplyr::select(LadlabID, Age, AgeGroup, Gender, Task, Response, SuccessorKnower, EndlessKnower, 
                IHC, FHC, DCE, Productivity)
```

Highest Next Number - commented because we're using highest contiguous
```{r}
# lookup <- full.data %>%
#   filter(Task == "WCN", 
#          Accuracy == 1)%>%
#   group_by(LadlabID)%>%
#   summarise(max = max(as.numeric(as.character(TaskItem)))) 
# 
# 
# #Add highest NN to model df
# add_highest_num <- function() {
#   tmp <- model.df
#   for (row in 1:nrow(tmp)) {
#     sub = as.character(tmp[row, "LadlabID"])
#     highest_num = subset(lookup, LadlabID == sub)$max
#     tmp[row, "Highest_NN"] = highest_num
#   }
#   return(tmp)
# }
# 
# #run this function on model df
# model.df <- add_highest_num()
```

Add highest contiguous next number to model.df 
```{r}
model.df <- right_join(model.df, highest_contiguous_nn, by = "LadlabID")

# hc.datawide <- right_join(hc.datawide, highest_contiguous_nn, by = "LadlabID")

# hc.datawide %>%
#   dplyr::select(LadlabID, Age, AgeGroup, productivity, max, 
#     HCReceivedSupport, ihc, dce, sup.noerror) %>%
#   group_by(productivity) %>%
#   summarize(median = median(max, na.rm=TRUE),
#             count = n())
# #median is 86 for all groups
```

Get mean WCN for everyone <span style="color:red">Not using this anymore - RMS</span>
```{r}
# lookup <- wcn.wide %>%
#   group_by(LadlabID)%>%
#   summarise(mean.NN = mean(immediate, na.rm = TRUE))
```

## Successor models
```{r}
#each participant only needs one row here, because we only need to know whether they are a Successor Knower or Endless Knower
distinct_model.df <- model.df %>%
  distinct(LadlabID, Age, AgeGroup, Gender, SuccessorKnower, EndlessKnower, 
           IHC, Highest_Contig_NN, FHC, DCE, Productivity)%>%
  mutate(SuccessorKnower = factor(SuccessorKnower, levels = c(0,1)), 
         EndlessKnower = factor(EndlessKnower, levels = c(0,1)))%>%
  mutate(IHC = as.integer(IHC), 
         Highest_Contig_NN = as.integer(Highest_Contig_NN), 
         LadlabID = factor(LadlabID))

# #add mean_nn to model df
# distinct_model.df <- right_join(distinct_model.df, lookup, by = "LadlabID")

###MODEL BUILDING AND COMPARISONS###
#base model for successor knower
base.successor <- glmer(SuccessorKnower ~ Age + (1|LadlabID), family = "binomial", 
                    data = distinct_model.df)

##IHC model##
model.ihc.successor <- glmer(SuccessorKnower ~ IHC + Age + (1|LadlabID), family = "binomial", 
                   data = distinct_model.df)
#convergence warnings, is this an issue?
with(model.ihc.successor@optinfo$derivs,max(abs(solve(Hessian,gradient)))<2e-3)#True, so we're okay

#compare
anova(base.successor, model.ihc.successor, test = 'LRT') #IHC not significant

##Highest NN Model##
model.nn.successor <- glmer(SuccessorKnower ~ Highest_Contig_NN + Age + (1|LadlabID), family = "binomial", 
                   data = distinct_model.df)

#compare
anova(base.successor, model.nn.successor, test = 'LRT')#highest contiguous NN not significant

##Productivity model##
model.prod.successor <- glmer(SuccessorKnower ~ Productivity + Age + (1|LadlabID), family = "binomial",
                   data = distinct_model.df)

#compare
anova(base.successor, model.prod.successor, test = 'LRT')#Productivity trending
```


## Endless Models
```{r}
base.endless <- glmer(EndlessKnower ~ Age + (1|LadlabID), family = "binomial", 
                      data = distinct_model.df)

###IHC MODEL###
model.ihc.endless <- glmer(EndlessKnower ~ IHC + Age + (1|LadlabID), family = "binomial", 
                        data = distinct_model.df)
#convergence warnings, is this an issue?
with(model.ihc.endless@optinfo$derivs,max(abs(solve(Hessian,gradient)))<2e-3)#true, so we're okay

#compare
anova(base.endless, model.ihc.endless, test = 'LRT') #IHC significant


###HIGHEST CONTIG NN MODEL###
model.nn.endless <- glmer(EndlessKnower ~ Highest_Contig_NN + Age + (1|LadlabID), family = "binomial", 
                        data = distinct_model.df) 
#convergence warnings, is this an issue?
with(model.nn.endless@optinfo$derivs,max(abs(solve(Hessian,gradient)))<2e-3)#True, model converging

anova(model.nn.endless, base.endless, test = 'LRT')#Highest contig NN significant

###PRODUCTIVITY MODEL###
model.prod.endless <- glmer(EndlessKnower ~ Productivity + Age + (1|LadlabID), family = "binomial", 
                            data = distinct_model.df)

#compare
anova(model.prod.endless, base.endless, test = 'LRT')#Prod significant

# #okay with about mean NN
# model2.endless <- glmer(EndlessKnower ~ mean.NN + Age + (1|LadlabID), family = "binomial", 
#                         data = distinct_model.df)
# anova(model2.endless, base.endless, test = 'LRT')#mean NN significant
```

### Endless: Large model comparison
Put all significant Endless predictors into large model, run model comparison
```{r}
large.endless.base <- glmer(EndlessKnower ~ IHC + Age + (1|LadlabID), 
                            family = "binomial", data = distinct_model.df)
#convergence warnings, is this an issue?
with(large.endless.base@optinfo$derivs,max(abs(solve(Hessian,gradient)))<2e-3)#True, we're okay

##add highest contig
large.endless.nn <- glmer(EndlessKnower ~ Highest_Contig_NN + IHC + (1|LadlabID), 
                          family = "binomial", data = distinct_model.df)

#compare
anova(large.endless.base, large.endless.nn, test = 'LRT')#Apparently ns?

##add productivity
large.endless.prod <- glmer(EndlessKnower ~ Productivity + IHC + (1|LadlabID), 
                          family = "binomial", data = distinct_model.df)
#convergence warnings, is this an issue?
with(large.endless.prod@optinfo$derivs,max(abs(solve(Hessian,gradient)))<2e-3)#True, we're okay

#compare 
anova(large.endless.base, large.endless.prod, test = 'LRT')#Productivity is significant

```

## JC testing removal of WCN failed practice
### Successor Models

```{r}
subset_distinct_model.df <- filter(distinct_model.df, Highest_Contig_NN>1)

###MODEL BUILDING AND COMPARISONS###
#base model for successor knower
subset_base.successor <- glmer(SuccessorKnower ~ Age + (1|LadlabID), family = "binomial", 
                    data = subset_distinct_model.df)

##IHC model##
subset_model.ihc.successor <- glmer(SuccessorKnower ~ IHC + Age + (1|LadlabID), family = "binomial", 
                   data = subset_distinct_model.df)
#convergence warnings, is this an issue?
with(subset_model.ihc.successor@optinfo$derivs,max(abs(solve(Hessian,gradient)))<2e-3)#True, so we're okay

#compare
anova(subset_base.successor, subset_model.ihc.successor, test = 'LRT') #IHC not significant

##Highest NN Model##
subset_model.nn.successor <- glmer(SuccessorKnower ~ Highest_Contig_NN + Age + (1|LadlabID), family =
"binomial", data = subset_distinct_model.df)
#convergence warnings, is this an issue?
with(subset_model.nn.successor@optinfo$derivs,max(abs(solve(Hessian,gradient)))<2e-3)#True, so we're okay

#compare
anova(subset_base.successor, subset_model.nn.successor, test = 'LRT')#highest contiguous NN not significant

##Productivity model##
subset_model.prod.successor <- glmer(SuccessorKnower ~ Productivity + Age + (1|LadlabID), family = "binomial", 
                   data = subset_distinct_model.df)

#compare
anova(subset_base.successor, subset_model.prod.successor, test = 'LRT')#Productivity trending
```


## Endless Models
```{r}
subset_base.endless <- glmer(EndlessKnower ~ Age + (1|LadlabID), family = "binomial", 
                      data = subset_distinct_model.df)

###IHC MODEL###
subset_model.ihc.endless <- glmer(EndlessKnower ~ IHC + Age + (1|LadlabID), family = "binomial", 
                        data = subset_distinct_model.df)

#convergence warnings, is this an issue?
with(subset_model.ihc.endless@optinfo$derivs,max(abs(solve(Hessian,gradient)))<2e-3)#true, so we're okay

#compare
anova(subset_base.endless, subset_model.ihc.endless, test = 'LRT') #IHC significant


###HIGHEST CONTIG NN MODEL###
subset_model.nn.endless <- glmer(EndlessKnower ~ Highest_Contig_NN + Age + (1|LadlabID), family = "binomial", 
                        data = subset_distinct_model.df) 

#convergence warnings, is this an issue?
with(subset_model.nn.endless@optinfo$derivs,max(abs(solve(Hessian,gradient)))<2e-3)#True, model converging

anova(subset_model.nn.endless, subset_base.endless, test = 'LRT')#Highest contig NN significant

###PRODUCTIVITY MODEL###
subset_model.prod.endless <- glmer(EndlessKnower ~ Productivity + Age + (1|LadlabID), family = "binomial", 
                            data = subset_distinct_model.df)

#compare
anova(subset_model.prod.endless, subset_base.endless, test = 'LRT')#Prod significant
```

### Endless: Large model comparison
Put all significant Endless predictors into large model, run model comparison
<span style="color:red">Question from JC: previous results indistinguishable when the 15 kids are removed; but here the very last comparison is ns. </span>
```{r}
subset_large.endless.base <- glmer(EndlessKnower ~ IHC + Age + (1|LadlabID), 
                            family = "binomial", data = subset_distinct_model.df)
#convergence warnings, is this an issue?
with(subset_large.endless.base@optinfo$derivs,max(abs(solve(Hessian,gradient)))<2e-3)#True, we're okay

##add highest contig
subset_large.endless.nn <- glmer(EndlessKnower ~ Highest_Contig_NN + IHC + (1|LadlabID), 
                          family = "binomial", data = subset_distinct_model.df)

#compare
anova(subset_large.endless.base, subset_large.endless.nn, test = 'LRT')#Apparently ns?

##add productivity
subset_large.endless.prod <- glmer(EndlessKnower ~ Productivity + IHC + (1|LadlabID), 
                          family = "binomial", data = subset_distinct_model.df)
#convergence warnings, is this an issue?
with(subset_large.endless.prod@optinfo$derivs,max(abs(solve(Hessian,gradient)))<2e-3)#True, we're okay

#compare 
anova(subset_large.endless.base, subset_large.endless.prod, test = 'LRT')#Productivity ns?

```
