---
title: "RecursionAnalysis"
author: "Junyi Chu, Rose M. Schneider, Pierina Cheung"
date: "`r Sys.Date()`"
output: github_document
---

# Setup
```{r setup, include=FALSE}
rm(list = ls())
require("knitr")

# # Set WD
# opts_knit$set(root.dir = "~/Sites/recursion/")
#opts_knit$set(root.dir = "~/Projects/Junyi study/recursiongithub/") #for PC
opts_knit$set(root.dir = "~/Documents/Projects/recursion/") #this is specific to RMS, change accordinglyz

# For wrapping lines when knitting
opts_chunk$set(tidy.opts=list(width.cutoff=80),tidy=TRUE,
               warning=FALSE)

library(Hmisc)
library(tidyverse)
library(magrittr)
#library(langcog)
library(lme4)
library(stringr)
library(RColorBrewer)
library(ggthemes)
library(memisc)

# Set seed for reproducible analyses
set.seed(42)
'%!in%' <- function(x,y)!('%in%'(x,y))
```

R Version for citation is: `r R.version.string`.

## Loading data
```{r}
#original data
full.data <- read.csv('data/recursion_full.csv', na.strings=c(""," ","NA", "NA "))
```

Reasons for exclusion and their numbers
```{r}
full.data %>%
  dplyr::filter(ExclusionGroup != "include") %>%
  dplyr::distinct(LadlabID, .keep_all = TRUE) %>%
  dplyr::group_by(ExclusionGroup) %>%
  dplyr::summarize(countN = dplyr::n_distinct(LadlabID)) %>%
  kable()
```


RMS original code for checking who failed practice - do not need to run. EVAL set to FALSE
```{r eval = FALSE}

# check how many failed both practice trials
x <- full.data %>%
  filter(Task == "WCN" &
           (TaskItem == 1 | TaskItem == 5))%>%
  group_by(LadlabID)%>%
  summarise(sum = sum(Accuracy))%>%
  filter(sum != 2)

#just hardcoding kids because it's easier than going back to the full data frame
#These kids got 1 right, 5 wrong: 
one.corr <- as.vector(c("012316-BO", "022616-JM", "030216-ED", 
                        "030817-ZI", "031516-A", "032216-JH", 
                        "032216-RC", "040317-AL", "040317-SL", 
                        "041316-AR", "041316-NC", "041316-VN", 
                        "062416-MC"))

five.corr <- as.vector("050617-Z1")

zero.corr <- as.vector(c("030216-AD", "040616-K"))


```

Exclude those who failed the practice trials on What Comes Next Task
```{r}

#final decision: remove kids who fail 1 trial out of 2 trials, with no additional information about whether E reran the failed trial. Removing 8 kids in total

# added 022516-ML on 2018-09-03 to the exclusion list. kid had NA data for wcn practice trials and 0 correct on test. assume kid failed wcn.

full.data %<>%
  mutate(ExclusionGroup = ifelse(LadlabID == "022616-JM"| LadlabID == "030216-AD"|
                                   LadlabID == "031516-A" | LadlabID == "041316-AR"|
                                   LadlabID == "041316-VN" | LadlabID == "032216-RC"|
                                   LadlabID == "012316-BO"| LadlabID == "041316-NC"|
                                   LadlabID == "022516-ML", "fail wcn", levels(ExclusionGroup)[ExclusionGroup]),
         ExclusionGroup = as.factor(ExclusionGroup))

# check. good
# full.data %>%
#   filter(LadlabID == "022616-JM")

```

Let's remove anyone who should not be included in the final dataset.
```{r}
full.data %<>%
  dplyr::filter(ExclusionGroup == "include")

```


Now, add in the Productivity classification, IHC, and FHC from PC, JC, and RMS coding

```{r}
#productivity, fhc, ihc coding from pc, jc, and rms
hc.data <- read.csv('data/HC-datawide-forcoding - hc.datawide.csv') %>%
  dplyr::select(LadlabID, prod_tomerge, ihc_tomerge, fhc_tomerge, dce)

full.data <- dplyr::left_join(full.data, hc.data, by = "LadlabID")

full.data %<>%
  dplyr::rename(Productivity = prod_tomerge, 
                IHC = ihc_tomerge, 
                FHC = fhc_tomerge, 
                DCE = dce)%>%
  dplyr::mutate(Productivity = factor(Productivity, levels = c("nonprod", "prod"), 
                                      labels = c("Nonproductive", "Productive")), 
                IHC = ifelse(IHC > 100, 100, IHC),
                FHC = ifelse(FHC > 100, 100, FHC))

#do a quick check to make sure we have the same SIDs in each
unique.full <- as.vector(unique(full.data$LadlabID))
unique.hc <- as.vector(unique(hc.data$LadlabID))

tmp <- hc.data %>%
  dplyr::filter(LadlabID %!in% unique.full)

#good to go - the only kids who are not included in full data are the ones who we excluded
```

Number of kids by age group and average age
```{r}
full.data %>%
  dplyr::group_by(AgeGroup) %>%
  dplyr::summarize(sumAge = n_distinct(LadlabID)) %>%
  kable()

full.data %>%
  dplyr::distinct(LadlabID, .keep_all = TRUE) %>%
  dplyr::summarize(minAge = min(Age),
                   maxAge = max(Age),
                   meanAge = mean(Age),
                   sdAge = sd(Age)) %>%
  kable()

```

Number of kids who were classified as decade productive & nonproductive
```{r}
full.data %>%
  dplyr::distinct(LadlabID, Productivity, Age)%>%
  dplyr::group_by(Productivity)%>%
  dplyr::summarise(n = n(),
                   meanage = mean(Age, na.rm=TRUE),
                   sdage = sd(Age, na.rm=TRUE),
                   minage = min(Age, na.rm=TRUE),
                   maxage = max(Age, na.rm=TRUE)) %>%
  kable()
```

Just for reference, this is the number of kids who switched classifications from PC, JC, RMS recode
```{r}
full.data %>%
  dplyr::filter(TaskType == "productivity") %>%
  droplevels()%>%
  dplyr::distinct(LadlabID, Response, Productivity) %>%
  dplyr::mutate(Response = factor(Response, levels = c("nonprod", "prod"), 
                                  labels = c("Nonproductive", "Productive")))%>%
  dplyr::mutate(changed_classification = ifelse((is.na(Response) & Productivity == "Nonproductive"),
                                                "NA_toNonprod",
                                                ifelse((is.na(Response) & Productivity == "Productive"), 
                                                       "NA_toProd", 
                                                       ifelse((Response == "Nonproductive" & Productivity == "Productive"), 
                                                              "Nonprod_toProd", 
                                                              ifelse((Response == "Productive" & Productivity == "Nonproductive"),
                                                                     "Prod_toNonprod", "no_change")))))%>%
  dplyr::group_by(changed_classification)%>%
  dplyr::summarise(n =n())
```

#Productivity gradient
```{r}
full.data %<>%
  mutate(delta.hc = FHC-IHC, 
         prod.gradient = delta.hc/(100-IHC), 
         prod.gradient = ifelse(IHC == 100, 1, as.numeric(prod.gradient)), 
         prod.gradient = ifelse(prod.gradient == 0 & IHC == 99, 1, as.numeric(prod.gradient)))
```

***
# Highest Count Descriptives
Average of IHC, DCE, and FHC for all kids
```{r}
full.data %>%
  dplyr::distinct(LadlabID, IHC)%>%
  dplyr::summarise(mean_IHC = mean(IHC),
                   sd_IHC = sd(IHC),
                   min_IHC = min(IHC),
                   max_IHC = max(IHC),
                   median_IHC = median(IHC)) %>%
  kable()

full.data %>%
  dplyr::distinct(LadlabID, DCE)%>%
  dplyr::summarise(mean_DCE = mean(DCE, na.rm=TRUE),
                   sd_DCE = sd(DCE, na.rm=TRUE),
                   min_DCE = min(DCE, na.rm=TRUE),
                   max_DCE = max(DCE, na.rm=TRUE),
                   median_DCE = median(DCE, na.rm=TRUE)) %>%
  kable()

full.data %>%
  dplyr::distinct(LadlabID, FHC)%>%
  dplyr::summarise(mean_FHC = mean(FHC),
                   sd_FHC = sd(FHC),
                   min_FHC = min(FHC),
                   max_FHC = max(FHC),
                   median_FHC = median(FHC)) %>%
  kable()

#productivity gradient
full.data %>%
  distinct(LadlabID, Productivity, delta.hc, prod.gradient)%>%
  group_by(Productivity)%>%
  summarise(mean_gradient = mean(prod.gradient), 
            sd_gradient = sd(prod.gradient), 
            mean_delta.hc = mean(delta.hc), 
            sd_delta.hc = sd(delta.hc))%>%
  kable()
```

Similar data by decade productivity
```{r}
full.data %>%
  dplyr::distinct(LadlabID, Productivity, IHC)%>%
  dplyr::group_by(Productivity)%>%
  dplyr::summarise(mean_IHC = mean(IHC),
                   sd_IHC = sd(IHC),
                   min_IHC = min(IHC),
                   max_IHC = max(IHC),
                   median_IHC = median(IHC)) %>%
  kable()

full.data %>%
  dplyr::distinct(LadlabID, Productivity, DCE)%>%
  dplyr::group_by(Productivity)%>%
  dplyr::summarise(mean_DCE = mean(DCE, na.rm=TRUE),
                   sd_DCE = sd(DCE, na.rm=TRUE),
                   min_DCE = min(DCE, na.rm=TRUE),
                   max_DCE = max(DCE, na.rm=TRUE),
                   median_DCE = median(DCE, na.rm=TRUE)) %>%
  kable()

full.data %>%
  dplyr::distinct(LadlabID, Productivity, FHC)%>%
  dplyr::group_by(Productivity)%>%
  dplyr::summarise(mean_FHC = mean(FHC),
                   sd_FHC = sd(FHC),
                   min_FHC = min(FHC),
                   max_FHC = max(FHC),
                   median_FHC = median(FHC)) %>%
  kable()
```


Plotting distribution of IHC, as a function of productivity (~ junyi's graph)

```{r}
unique.hc.data <- full.data %>%
  dplyr::distinct(LadlabID, Gender, Age, AgeGroup, HCReceivedSupport, IHC, DCE, FHC, Productivity)

ggplot(unique.hc.data, aes(x=IHC, color=Productivity)) + 
  geom_dotplot(aes(fill = Productivity),
               binwidth=1, stackgroups=TRUE, binpositions="all",method="dotdensity", dotsize = 1) +
  scale_color_brewer(palette="Set1") + 
  scale_fill_brewer(palette="Set1") +
  coord_fixed(ratio=1) +
  scale_y_continuous(breaks=seq(0,40,10), lim=c(0,35)) +
  scale_x_continuous(breaks=seq(0,100,by=10)) +
  labs(x="IHC", 
       y="Frequency") +
  theme_bw(base_size = 13) + 
  theme(legend.position="bottom", 
        legend.title = element_blank(), 
        panel.grid.minor = element_blank())
ggsave('graphs/ihc-by-prod.png')
# hist(unique.hc.data$IHC)

#trying with bars, doesn't look better
# ggplot(unique.hc.data, aes(x=IHC, fill=Productivity)) + 
#   geom_histogram(binwidth = 1, colour = "black") +
#   scale_fill_brewer(palette="Set1") +
#   coord_fixed(ratio=1) +
#   # scale_y_continuous(breaks=seq(0,40,10), lim=c(0,35)) +
#   scale_x_continuous(breaks=seq(0,100,by=10)) +
#   labs(x="IHC", 
#        y="Frequency") +
#   theme_bw(base_size = 13) + 
#   theme(legend.position="bottom", 
#         legend.title = element_blank(), 
#         panel.grid.minor = element_blank())
# ggsave('graphs/ihc-by-prod.png')
# # hist(unique.hc.data$IHC)
```

Plotting productivity as a function of age in months

```{r}
unique.hc.data$AgeMonths = floor(unique.hc.data$Age*12)

ggplot(unique.hc.data, aes(x=AgeMonths, colour = Productivity)) + 
  geom_dotplot(aes(fill = Productivity),
               binwidth = 1,
               stackgroups=TRUE, binpositions="all") +
  coord_fixed(ratio=1) +
  scale_y_continuous(breaks=seq(0,10,5), lim=c(0,12)) +
  scale_x_continuous(breaks=seq(48,72,by=6)) +
  scale_color_brewer(palette="Set1") + 
  scale_fill_brewer(palette="Set1") +
  labs( x="Age in Months", 
       y="Frequency") +
  theme_bw(base_size = 13) + 
  theme(legend.position="bottom")
ggsave('graphs/prod-by-age.png')

```

## Distance between IHC and FHC

Restructure data to plot distance between IHC, DCE, and FHC
```{r}
hc.dev.data <- full.data %>%
  dplyr::select(LadlabID, Age, Productivity, IHC, DCE, FHC, prod.gradient) %>%
  gather(hcprogression, hc, IHC:FHC)%>%
  mutate(hcprogression = factor(hcprogression, levels = c("IHC", "DCE", "FHC"))) %>%
  dplyr::rename(`Highest Count Coding` = hcprogression)

#all kids together
ggplot(hc.dev.data, aes(x = LadlabID, y = hc)) + 
  facet_grid(rows = vars(Productivity)) +
  geom_line(data=hc.dev.data[!is.na(hc.dev.data$hc),]) + 
  geom_point(aes(shape = `Highest Count Coding`, colour = `Highest Count Coding`), 
             size = 2, stroke = 1.5) +
  scale_color_brewer(palette="Dark2") +
  scale_shape_manual(values = c(4,5,20)) +
  labs(title="Highest Count Progression by Decade Productivity",
       x = "Each line = individual participant",
       y="Highest Count by Count Type") +
  theme_bw(base_size = 13) + 
  theme(legend.position="bottom", 
        axis.text.x = element_text(angle = 270, hjust = 1)) +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) 

hc.dev.prod <- subset(hc.dev.data, Productivity == "Productive")
hc.dev.nonprod <- subset(hc.dev.data, Productivity == "Nonproductive")
```


Separate graphs for productivity groups (for easier viewing)
```{r eval=FALSE, include=FALSE}
#productive
ggplot(hc.dev.prod, aes(x = LadlabID, y = hc)) + 
  facet_grid(rows = vars(Productivity)) +
  geom_line(data=hc.dev.prod[!is.na(hc.dev.prod$hc),]) + 
  geom_point(aes(shape = `Highest Count Coding`, colour = `Highest Count Coding`), 
             size = 2, stroke = 1.5) +
  scale_color_brewer(palette="Dark2") +
  scale_shape_manual(values = c(4,5,20)) +
  ylim(0, 100) +
  labs(title="A. Distance, Productive Decade Counters",
       x = "Each line = individual participant",
       y="Highest Count") +
  theme_bw(base_size = 13) + 
  theme(legend.position="bottom", 
        axis.text.x = element_text(angle = 270, hjust = 1)) + 
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
ggsave('graphs/distance-prod.png')

#nonproductive
ggplot(hc.dev.nonprod, aes(x = LadlabID, y = hc)) + 
  facet_grid(rows = vars(Productivity)) +
  geom_line(data=hc.dev.nonprod[!is.na(hc.dev.nonprod$hc),]) + 
  geom_point(aes(shape = `Highest Count Coding`, colour = `Highest Count Coding`), 
             size = 2, stroke = 1.5) +
  scale_color_brewer(palette="Dark2") +
  scale_shape_manual(values = c(4,5,20)) +
  ylim(0, 100) +
  labs(title="B. Distance, Non-productive Decade Counters",
       x = "Each line = individual participant",
       y="Highest Count") +
  theme_bw(base_size = 13) + 
  theme(legend.position="bottom", 
        axis.text.x = element_text(angle = 270, hjust = 1)) +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
ggsave('graphs/distance-nonprod.png')

```

Separate graphs for productivity groups, sorted by ascending IHC
```{r}
#productive
ggplot(hc.dev.prod, aes(x = reorder(LadlabID, hc, FUN=min), y = hc)) + 
  facet_grid(rows = vars(Productivity)) +
  geom_line(data=hc.dev.prod[!is.na(hc.dev.prod$hc),]) + 
  geom_point(aes(shape = `Highest Count Coding`, colour = `Highest Count Coding`), 
             size = 2, stroke = 1.5) +
  scale_color_brewer(palette="Dark2") +
  scale_shape_manual(values = c(4,5,20)) +
  ylim(0, 100) +
  labs(x = "Each line = individual participant",
       y="Highest Count") +
  theme_bw(base_size = 13) + 
  theme(legend.position="bottom", 
        axis.text.x = element_text(angle = 270, hjust = 1)) + 
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
ggsave('graphs/distance-prod-sorted.png')

#nonproductive
ggplot(hc.dev.nonprod, aes(x = reorder(LadlabID, hc, FUN=min), y = hc)) + 
  facet_grid(rows = vars(Productivity)) +
  geom_line(data=hc.dev.nonprod[!is.na(hc.dev.nonprod$hc),]) + 
  geom_point(aes(shape = `Highest Count Coding`, colour = `Highest Count Coding`), 
             size = 2, stroke = 1.5) +
  scale_color_brewer(palette="Dark2") +
  scale_shape_manual(values = c(4,5,20)) +
  ylim(0, 100) +
  labs(x = "Each line = individual participant",
       y="Highest Count") +
  theme_bw(base_size = 13) + 
  theme(legend.position="bottom", 
        axis.text.x = element_text(angle = 270, hjust = 1)) +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
ggsave('graphs/distance-nonprod-sorted.png')

```

Number of kids who counted to 99+ spontaneously on IHC plus those whose FHC = 99+ without prompting
```{r}
# full.data %>%
#   filter(IHC > 98) %>%
#   distinct(LadlabID, IHC, FHC, HCReceivedSupport) %>%
#   count() #n=32
# but some kids made errors past IHC but < 3 so need to account for that

  filter(FHC > 98 & (is.na(HCReceivedSupport)|HCReceivedSupport != 1)) %>%
  distinct(LadlabID, IHC, FHC, HCReceivedSupport) %>%
  count() #n =42

```

## Decade prompts
Average number of decade prompts provided. Productive counters first
```{r}
full.data %>%
  filter(TaskItem == "times") %>%
  filter(Productivity == "Productive") %>%
  distinct(LadlabID, HCReceivedSupport, TaskItem, Response) %>%
  mutate(Response = as.numeric(levels(Response)[Response])) %>%
  group_by(HCReceivedSupport) %>%
  summarize(mean = mean(Response, na.rm=TRUE),
            sd = sd(Response, na.rm=TRUE),
            min = min(Response, na.rm=TRUE),
            max = max(Response, na.rm=TRUE),
            count=n())
# assume 0 = NA
# error in supported.times coding, should only count to 90
# but one kid got prompted with 100 and 110 and times should be 0

```


Then nonproductive counters.
```{r}
full.data %>%
  filter(TaskItem == "times") %>%
  filter(Productivity == "Nonproductive") %>%
  distinct(LadlabID, HCReceivedSupport, TaskItem, Response) %>%
  mutate(Response = as.numeric(levels(Response)[Response])) %>%
  group_by(HCReceivedSupport) %>%
  summarize(mean = mean(Response, na.rm=TRUE),
            sd = sd(Response, na.rm=TRUE),
            min = min(Response, na.rm=TRUE),
            max = max(Response, na.rm=TRUE),
            count=n())
# assume 0 = NA
# error in supported.times coding, should only count to 90
# but one kid got prompted with 100 and 110 and times should be 0
```


# What Comes Next Descriptives

<span style="color:red">Note minimum highest contig NN can be 5 (one of the practice trials). Practice trials are excluded from %corr and within vs. beyond computation.</span>

First check if Accuracy column in full.data is coded correctly. Good to go.
```{r}
wcn.data <- full.data %>%
  filter(Task == "WCN")

wcn.data %<>%
  mutate(Response_num = as.numeric(as.character(Response)), 
         TaskItem_num = as.numeric(as.character(TaskItem)), 
         Accuracy_check = ifelse(Response_num == (TaskItem_num + 1), 1, 0), 
         Accuracy_valid = ifelse(Accuracy == Accuracy_check, TRUE, FALSE))

validate <- function(){
  validation <- wcn.data %>%
    filter(Accuracy_valid == FALSE)
  if(length(validation$LadlabID) > 0) {
    print("WARNING: CHECK CODING")
  } else {
    print("All coding correct")
  }
}

validate()
```

Immediate vs. Momentum trials: Children were provided with momentum trials if they got wrong on immediate trials. Check %trials where immediate = wrong, momentum = right
```{r}
wcn.wide <- full.data %>%
  filter(ExclusionGroup == "include") %>%
  filter(Task == "WCN") %>%
  filter(TaskType != "practice") %>%
  filter(TaskItem != 3) %>% # a trial on 3 for momentum that doesn't exist for immediate
  droplevels()%>%
  dplyr::select(LadlabID, Age, AgeGroup, TaskType, TaskItem, Accuracy, Productivity, prod.gradient) %>%
  spread(TaskType, Accuracy)

# data check: some kids got 1 for immediate but 0 for momentum or 1 for immediate and 1 for momentum (N = 5).Keeping them. 
## for reference, pulling out these kids below
full.data %>%
  filter(Task == "WCN", 
         TaskType == "momentum" | TaskType == "immediate")%>%
  dplyr::select(LadlabID, Age, AgeGroup, TaskType, TaskItem, Accuracy) %>%
  spread(TaskType, Accuracy)%>%
  mutate(issue_immediate1Momentum0 = ifelse(immediate == 1 & momentum == 0, TRUE, FALSE), 
         issue_immediate1Momentum1 = ifelse(immediate == 1 & momentum == 1, TRUE, FALSE))%>%
  filter(issue_immediate1Momentum0 == TRUE | 
           issue_immediate1Momentum1 == TRUE)

# how many kids show improved performance
xtabs(~immediate + momentum, data = wcn.wide, na.action = na.pass, exclude = NULL)
# 191 / 1048 trials = ~ 18%. NOTE % not by kids but by trials.
```

Percent Correct on WCN
```{r}
wcn.data %>%
  dplyr::filter(TaskType == "immediate") %>%
  dplyr::group_by(LadlabID) %>%
  dplyr::summarize(avg.wcn = mean(Accuracy, na.rm=TRUE),
                   sd.wcn = sd(Accuracy, na.rm=TRUE)) %>%
  dplyr::summarize(avg = mean(avg.wcn),
                   sd = sd(sd.wcn))

wcn.data %>%
  dplyr::filter(TaskType == "immediate") %>%
  dplyr::group_by(LadlabID, Productivity) %>%
  dplyr::summarize(avg.wcn = mean(Accuracy, na.rm=TRUE),
                   sd.wcn = sd(Accuracy, na.rm=TRUE)) %>%
  dplyr::group_by(Productivity) %>%
  dplyr::summarize(avg = mean(avg.wcn),
                   sd = sd(sd.wcn))
```

Plotting %corr on WCN as function of productivity
```{r}
wcn.data %>%
  dplyr::filter(TaskType == "immediate") %>%
  dplyr::group_by(LadlabID, Productivity, prod.gradient) %>%
  dplyr::summarize(avg.wcn = mean(Accuracy, na.rm=TRUE),
                   sd.wcn = sd(Accuracy, na.rm=TRUE)) %>%
  ggplot(aes(x = Productivity, y = avg.wcn, fill=factor(Productivity))) +
  stat_summary(fun.y = mean, position = position_dodge(width = .95), 
               geom="bar", alpha = .8, colour = "black") +
  geom_violin(alpha = .3) +
  stat_summary(fun.data = mean_se, geom="errorbar", 
               position = position_dodge(width=0.90), width = 0.2)+
  #scale_fill_discrete(name = "Productivity") +
  scale_fill_brewer(name = "Productivity", palette = "Set1", guide = "none") +
  scale_colour_brewer(palette = "Greys") +
  ylab("Proportion Correct") + 
  xlab('Productivity') + 
  theme_bw(base_size = 13) + 
  theme(legend.position = "none", 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  theme(text = element_text(size = 12)) +
  ylim(0, 1.0) 
  
  
ggsave('graphs/wcn-percentcorr.png')


```

Add whether the Task Item was within or outside of the kid's initial highest count.
```{r}
#first, get initial highest count for each kiddo
#Make a lookup table with SID and initial highest count
lookup <- full.data %>%
  distinct(LadlabID, IHC)

wcn.data %<>%
  dplyr::mutate(TaskItem = as.numeric(as.character(TaskItem)))

#This is a function that, for each trial, checks the number queried. If number queried is above the child's initial highest count, marks that trial as beyond count range.
determine_count_range <- function(df) {
  tmp <- df
  for (row in 1:nrow(tmp)) {
    sub = as.character(tmp[row, "LadlabID"])
    count_range = as.numeric(as.character(subset(lookup, LadlabID == sub)$IHC))
    tmp[row, "IHC"] = as.numeric(as.character(count_range))
    if (tmp[row, "TaskItem"] > count_range) {
      tmp[row, "WithinOutsideIHC"] = "outside"
    } else {
      tmp[row, "WithinOutsideIHC"] = "within"
    }
  }
  return(tmp)
}

#Run for wcn
wcn.data <- determine_count_range(wcn.data)
```

WCN accuracy, within and outside of IHC
```{r}
wcn.data %>%
  dplyr::filter(TaskType == "immediate") %>%
  dplyr::group_by(WithinOutsideIHC) %>%
  dplyr::summarize(mean = mean(Accuracy, na.rm = TRUE), 
                   sd = sd(Accuracy, na.rm = TRUE))
```


Now WCN by within/outside count range and productivity
```{r}
wcn.data %>%
  dplyr::filter(TaskType == "immediate") %>%
  dplyr::group_by(Productivity, WithinOutsideIHC) %>%
  dplyr::summarize(mean = mean(Accuracy, na.rm = TRUE), 
                   sd = sd(Accuracy, na.rm = TRUE))
```


Plotting WCN as within vs. beyond by productivity 
```{r}
wcn.data %>%
  dplyr::filter(TaskType == "immediate") %>%
  dplyr::group_by(Productivity, WithinOutsideIHC, LadlabID) %>%
  dplyr::summarize(meansubj = mean(Accuracy, na.rm = TRUE)) %>%
  ggplot(aes(x=WithinOutsideIHC, y=meansubj, fill=Productivity)) +
  stat_summary(fun.y = mean, position = position_dodge(width = .95), 
               geom="bar", colour = "black") +
  stat_summary(fun.data = mean_se, geom="errorbar",
               position = position_dodge(width=0.90), width = 0.2) +
  scale_fill_brewer(name = "Productivity", palette="Set1") +
  scale_y_continuous(lim=c(0,1)) +
  labs(y="Proportion Correct", 
       fill="Productivity") +
  theme_bw() +
  theme(text = element_text(size = 12))

ggsave('graphs/wcn-within-beyond.png')

prod.pal.1 <- c("#880f10","#214B6E")

wcn.data %>%
  mutate(WithinOutsideIHC = factor(WithinOutsideIHC, levels = c("within", "outside"), 
                                   labels = c("Within", "Outside")))%>%
  dplyr::filter(TaskType == "immediate") %>%
  dplyr::group_by(Productivity, WithinOutsideIHC, LadlabID, prod.gradient) %>%
  dplyr::summarize(meansubj = mean(Accuracy, na.rm = TRUE)) %>%
  ggplot(aes(x=Productivity, y=meansubj, fill=WithinOutsideIHC)) +
  geom_violin(alpha=0.7, scale="count", position=position_dodge(width=0.8)) +
  geom_point(aes(colour = Productivity), position=position_jitterdodge(jitter.width=0.25, 
                                                                       jitter.height = .1, 
                                                                       dodge.width=.9), 
             alpha = .7) +
  stat_summary(fun.y = mean,position = position_dodge(width=0.8), 
               geom="point", shape=23, size=3, colour = "black") +
  stat_summary(fun.data = mean_cl_boot, geom="errorbar",
               position = position_dodge(width=0.8), width = 0.2) +  
  scale_fill_brewer(name = "Trial Type", palette="Dark2",direction=-1) +
  scale_colour_manual(values = prod.pal.1, guide = "none") + 
  scale_y_continuous(limits=c(0,1)) +
  labs(y="Average Proportion Correct", x="",
       fill="Trial Type") +
  theme_bw(base_size = 13) +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank())

ggsave('graphs/wcn-within-beyond2.png', width=6, height=4)
```

Analysis of WCN accuracy by productivity and trial type
```{r}
# wcn_score.df <- wcn.data %>%
#   dplyr::filter(TaskType == "immediate") %>%
#   dplyr::group_by(LadlabID, Productivity, TrialType=as.factor(WithinOutsideIHC)) %>%
#   dplyr::summarize(correct = sum(Accuracy, na.rm = TRUE), total=n())
# 
wcn_model.df <- wcn.data %>%
  filter(TaskType == "immediate")%>%
  mutate(IHC = as.integer(IHC),
         LadlabID = factor(LadlabID))%>%
  mutate(IHC.c = as.vector(scale(IHC, center = TRUE, scale=TRUE)), #scale and center for model fit
         FHC.c = as.vector(scale(FHC, center = TRUE, scale=TRUE)), 
         age.c = as.vector(scale(Age, center = TRUE, scale=TRUE)))

##WCN model looking at interaction between productivity and trial type in WCN task
wcn.model.base <- glmer(Accuracy ~ age.c + (1|TaskItem) + (1|LadlabID), 
                        family = "binomial", data = wcn_model.df)
wcn.model.ihc <- glmer(Accuracy ~ IHC.c + age.c + (1|TaskItem) + (1|LadlabID), 
                       family = "binomial", data = wcn_model.df)
wcn.model.noint <- glmer(Accuracy ~ Productivity + WithinOutsideIHC + IHC.c + age.c + (1|TaskItem) +
                     (1|LadlabID), family = "binomial", data = wcn_model.df)
wcn.model.int <- glmer(Accuracy ~ Productivity+ WithinOutsideIHC + 
                         Productivity:WithinOutsideIHC + IHC.c + age.c + (1|TaskItem) +
                     (1|LadlabID), family = "binomial", data = wcn_model.df)

#comparison of models
anova(wcn.model.int, wcn.model.noint, wcn.model.ihc, wcn.model.base, test = 'LRT')
```


How many trials do kids have beyond their IHC?
```{r}
wcn.data %>%
  dplyr::filter(TaskType == "immediate") %>%
  dplyr::group_by(Productivity, WithinOutsideIHC)%>%
  dplyr::summarise(n = n())
```

## Highest contiguous NN

```{r}
wcn.wide %<>%
  dplyr::mutate(TaskItem = as.numeric(as.character(TaskItem)))

unique.nn <- as.vector(unique(wcn.wide$LadlabID))
#get the task items from wcn
nextnums <- as.vector(unique(wcn.wide$TaskItem))

#this is a function that pulls out the largest number for which a participant had a correct consecutive
get_contiguous <- function(){
  contig <- data.frame()
  for (sub in unique.nn) {
    tmp <- wcn.wide %>%
      dplyr::select(LadlabID, Age, AgeGroup, TaskItem, immediate)%>%
      filter(LadlabID == sub, 
             immediate == 0)%>%
      mutate(TaskItem = sort(TaskItem))
    if (length(tmp$LadlabID) == 0) {
      highest_contig = 86
      sub_contig <- data.frame(sub, highest_contig)
      contig <- bind_rows(contig, sub_contig)
    } else if (length(tmp$TaskItem) > 0 & min(tmp$TaskItem) == 23) {
      #if(sub %in% one.corr){
      highest_contig = 5
      sub_contig <- data.frame(sub, highest_contig)
      contig <- bind_rows(contig, sub_contig)
      # } else if(sub %in% five.corr | sub %in% zero.corr){
      #   highest_contig = 0
      #   sub_contig <- data.frame(sub, highest_contig)
      #   contig <- bind_rows(contig, sub_contig)
      # } else {
      #   highest_contig = 5
      #   sub_contig <- data.frame(sub, highest_contig)
      #   contig <- bind_rows(contig, sub_contig)
      # }
    } else {
      min.nn <- min(tmp$TaskItem)
      prev_correct <- nextnums[nextnums < min.nn]
      highest_contig <- max(prev_correct)
      
      sub_contig <- data.frame(sub,
                               highest_contig)
      contig <- bind_rows(contig, sub_contig)
    }
  }
  return(contig)
}

highest_contiguous_nn <- get_contiguous()%>%
  dplyr::rename(LadlabID = sub)%>%
  distinct(LadlabID, highest_contig)%>%
  dplyr::rename(Highest_Contig_NN = highest_contig)

#add highest contiguous to wcn.data
wcn.data <- full_join(wcn.data, highest_contiguous_nn, by = "LadlabID")

```

Code for checking highest contig NN
```{r eval = FALSE}
full.data %>%
  # filter(LadlabID == "022316-AB") %>%
  filter(TaskType == "immediate"|TaskType == "practice") %>%
  dplyr::select(LadlabID, TaskType, TaskItem, Accuracy)

# these two kids, for example, had the same contig highest NN but diff profile of responses
#040317-KK #7 correct out of 10
#022316-AB #9 correct out of 10


# wcn.data %<>%
#   dplyr::right_join(highest_contiguous_nn) 
# 
# wcn.data %>%
#   filter(LadlabID == "040317-KK")

```

See if highest contiguous next number underestimates kids' knowledge. Seems to correspond well with # correct data.
```{r}
wcn.data %>%
  dplyr::filter(TaskType == "immediate"|TaskType == "practice") %>% #added prac for 1&5
  dplyr::group_by(LadlabID, Highest_Contig_NN) %>%
  dplyr::summarize(n_corr = sum(Accuracy, na.rm = TRUE)) %>%
  dplyr::group_by(Highest_Contig_NN, n_corr) %>%
  dplyr::summarize(n_participants = n_distinct(LadlabID)) %>%
  tidyr::spread(n_corr, n_participants) %>%
  kable()


# 2 kids had NA as n_corr
wcn.data %>%
  dplyr::filter(TaskType == "immediate"|TaskType == "practice") %>% #added prac for 1&5
  dplyr::group_by(LadlabID, Highest_Contig_NN) %>%
  dplyr::summarize(n_corr = sum(Accuracy)) %>%
  dplyr::group_by(Highest_Contig_NN, n_corr) %>%
  filter(is.na(n_corr))
# 022516-ML
# 040317-SL

# this kid (ML) got 0 for all test and NA for 1 and 5. Not one of the two kids under zero.corr because kid's sum is NA. Now excluded up top.

# commentout
# full.data %>%
#   filter(LadlabID == "022516-ML") %>%
#   filter(TaskType == "immediate"|TaskType == "practice") %>%
#   select(LadlabID, TaskType, TaskItem, Accuracy)

# this kid (SL) has one NA value but otherwise look fine
# now added na.rm=TRUE for sum(accuracy)

# commentout
# full.data %>%
#   filter(LadlabID == "040317-SL") %>%
#   filter(TaskType == "immediate"|TaskType == "practice") %>%
#   select(LadlabID, TaskType, TaskItem, Accuracy)

# overview of highest contiguous coding and by-trial performance
z <- wcn.data %>%
  dplyr::right_join(highest_contiguous_nn) %>%
  filter(TaskType == "immediate") %>%
  dplyr::select(LadlabID, Highest_Contig_NN, TaskItem, Accuracy) %>%
  spread(TaskItem, Accuracy)
```

Median highest contiguous next number by productivity  - minus kids who counted to 99 spontaneously
```{r}
wcn.data %>%
  filter(IHC < 99)%>%
  dplyr::distinct(LadlabID, Highest_Contig_NN, Productivity) %>%
  dplyr::group_by(Productivity) %>%
  dplyr::summarise(n = n(),
                   median_NN = median(Highest_Contig_NN),
                   mean_NN = mean(Highest_Contig_NN)) %>%
  kable()

```

Plotting freq of highest contiguous as a function of productivity
``` {r}
full.data %>%
  dplyr::right_join(highest_contiguous_nn) %>%
  dplyr::distinct(LadlabID, Highest_Contig_NN, Productivity) %>%
  ggplot(aes(x=Highest_Contig_NN, color=Productivity)) + 
  geom_dotplot(aes(fill = Productivity),
               binwidth=1, stackgroups=TRUE, binpositions="all",method="dotdensity") +
  scale_color_brewer(palette="Set1") + 
  scale_fill_brewer(palette="Set1") +
  coord_fixed(ratio=1) +
  scale_y_continuous(breaks=seq(0,50,10), lim=c(0,50)) +
  #scale_x_continuous(breaks=seq(0,100,by=10)) +
  scale_x_continuous(breaks = c(0, 1, 5, 23, 29, 37, 40, 62, 70, 86),
                     labels=c("0", "1", "5", "23", "29", "37", "40", "62", "70", "86")) +
  labs(x="Highest Contiguous Next Number", 
       y="Frequency") +
  theme_bw() + 
  theme(legend.position="bottom")
ggsave('graphs/highestcontig-by-prod.png')

# side by side
full.data %>%
  dplyr::right_join(highest_contiguous_nn) %>%
  dplyr::distinct(LadlabID, Highest_Contig_NN, Productivity) %>%
  ggplot(aes(x=Highest_Contig_NN, color=Productivity)) + 
  geom_dotplot(aes(fill = Productivity),
               binwidth=1, stackdir="up", position=position_dodge(width=2), stackgroups=FALSE, binpositions="all",method="dotdensity") +
  scale_color_brewer(palette="Set1") + 
  scale_fill_brewer(palette="Set1") +
  coord_fixed(ratio=1) +
  scale_y_continuous(breaks=seq(0,30,10), lim=c(0,30)) +
  #scale_x_continuous(breaks=seq(0,100,by=10)) +
  scale_x_continuous(breaks = c(0, 1, 5, 23, 29, 37, 40, 62, 70, 86),
                     labels=c("0", "1", "5", "23", "29", "37", "40", "62", "70", "86")) +
  labs(x="Highest Contiguous Next Number", 
       y="Frequency") +
  theme_bw() + 
  theme(legend.position="bottom")
ggsave('graphs/highestcontig-by-prod-2.png')
```


Correlations
```{r}
corrdf <- full.data %>%
  dplyr::right_join(highest_contiguous_nn) %>%
  dplyr::distinct(LadlabID, Highest_Contig_NN, Age, IHC, FHC) %>%
  dplyr::select(-LadlabID)

rcorr(as.matrix(corrdf), type = "pearson")
```

# Infinity Descriptives

Number of kids in each infinity category
```{r}
full.data %>%
  dplyr::distinct(LadlabID, Category)%>%
  dplyr::group_by(Category)%>%
  dplyr::summarise(n = n())

classification.data <- full.data %>%
  dplyr::distinct(LadlabID, EndlessKnower, SuccessorKnower, Productivity)

#Successor contingency table
table(classification.data$SuccessorKnower, classification.data$Productivity)
chisq.test(table(classification.data$SuccessorKnower, classification.data$Productivity))

#Endless contingency table
table(classification.data$EndlessKnower, classification.data$Productivity)
chisq.test(table(classification.data$EndlessKnower, classification.data$Productivity))
```

Average age of kids for Endless and Successor Knowers
```{r}
full.data %>%
  dplyr::distinct(LadlabID, SuccessorKnower, Age)%>%
  dplyr::group_by(SuccessorKnower)%>%
  dplyr::summarise(meanAge = mean(Age),
                   sdAge = sd(Age),
                   meanAgeMonths = mean(Age)*12,
                   sdAgeMonths = sd(Age)*12)

full.data %>%
  dplyr::distinct(LadlabID, EndlessKnower, Age)%>%
  dplyr::group_by(EndlessKnower)%>%
  dplyr::summarise(meanAge = mean(Age),
                   sdAge = sd(Age),
                   meanAgeMonths = mean(Age)*12,
                   sdAgeMonths = sd(Age)*12)

```

Infinity in relation to highest count
```{r}
full.data %>%
  dplyr::distinct(LadlabID, EndlessKnower, IHC, FHC) %>%
  dplyr::group_by(EndlessKnower) %>%
  dplyr::summarize(mean_IHC = mean(IHC),
                   mean_FHC = mean(FHC))

full.data %>%
  dplyr::distinct(LadlabID, SuccessorKnower, IHC, FHC) %>%
  dplyr::group_by(SuccessorKnower) %>%
  dplyr::summarize(mean_IHC = mean(IHC),
                   mean_FHC = mean(FHC))
```

Infinity in relation to WCN
```{r}
full.data %>%
  dplyr::right_join(highest_contiguous_nn) %>%
  dplyr::distinct(LadlabID, EndlessKnower, Highest_Contig_NN) %>%
  dplyr::group_by(EndlessKnower) %>%
  dplyr::summarize(mean_contig_nn = mean(Highest_Contig_NN),
                   median_contig_nn = median(Highest_Contig_NN))


full.data %>%
  dplyr::right_join(highest_contiguous_nn) %>%
  dplyr::distinct(LadlabID, SuccessorKnower, Highest_Contig_NN) %>%
  dplyr::group_by(SuccessorKnower) %>%
  dplyr::summarize(mean_contig_nn = mean(Highest_Contig_NN),
                   median_contig_nn = median(Highest_Contig_NN))



```

#Correlation between productivity gradient and IHC/FHC
```{r}
ms.cor <- full.data %>%
  distinct(LadlabID, Age, IHC, FHC, prod.gradient)

cor.test(ms.cor$IHC, ms.cor$prod.gradient) #sig. correlation between IHC and prod. gradient
cor.test(ms.cor$FHC, ms.cor$prod.gradient) #sig. correlation between FHC and prod. gradient

```

#Correlation between Productivity classification and Prod.gradient
```{r}
ms.cor <- full.data %>%
  dplyr::distinct(LadlabID, Productivity, prod.gradient)%>%
  mutate(Productivity = factor(Productivity, levels = c("Productive", "Nonproductive"),
                             labels = c(1, 0)), 
         Productivity = as.integer(as.character(Productivity)))

cor.test(ms.cor$Productivity, ms.cor$prod.gradient)
```

#Jess graph
```{r}
prod.pal <- c("#E41A1C", "#4DAF4A", "#377EB8")

wcn.data %>%
  mutate(prod.group = ifelse(IHC > 99, "Productive (IHC > 99)", 
                             ifelse(Productivity == "Productive", "Productive (IHC < 99)", "Nonproductive")))%>%
  filter(TaskType == "immediate")%>%
  mutate(TaskItem == factor(TaskItem))%>%
  group_by(TaskItem, prod.group)%>%
   summarise(mean = mean(Accuracy, na.rm = TRUE), 
            n = n(), 
            sd = sd(Accuracy, na.rm = TRUE), 
            se = sd/sqrt(n)) %>%
  ggplot(aes(x = factor(TaskItem), y = mean, colour = prod.group, group= prod.group)) +
  geom_point(size = 2.5) + 
  geom_line(size = .7) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), 
                width = 0, size = .5) +
  theme_bw(base_size = 13) + 
  scale_colour_manual(values = prod.pal) +
  theme(legend.position = "right", legend.title = element_blank()) +
  labs(x = "Task item", y = "Mean performance") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

# Analyses
## Counting, Productivity, and Infinity Battery
To identify whether there is connection between counting experience and Infinity Task performance, we will conduct three initial analyses, predicting Infinity Task performance from either (1) Initial Highest Count, (2) Productivity for Decade Rule (defined above), or (3) performance on the Next Number task. 

glm(inf.0/1 ~ (predictor) + age, family = binomial).

---
First, we need to make a model data frame that readily has all of this information

```{r}
#model base
model.df <- full.data %>%
  dplyr::select(LadlabID, Age, AgeGroup, Gender, Task, Response, SuccessorKnower, EndlessKnower, 
                IHC, FHC, DCE, Productivity, prod.gradient)
```

Highest Next Number - commented because we're using highest contiguous
```{r}
# lookup <- full.data %>%
#   filter(Task == "WCN", 
#          Accuracy == 1)%>%
#   group_by(LadlabID)%>%
#   summarise(max = max(as.numeric(as.character(TaskItem)))) 
# 
# 
# #Add highest NN to model df
# add_highest_num <- function() {
#   tmp <- model.df
#   for (row in 1:nrow(tmp)) {
#     sub = as.character(tmp[row, "LadlabID"])
#     highest_num = subset(lookup, LadlabID == sub)$max
#     tmp[row, "Highest_NN"] = highest_num
#   }
#   return(tmp)
# }
# 
# #run this function on model df
# model.df <- add_highest_num()
```

Add highest contiguous next number to model.df 
```{r}
model.df <- right_join(model.df, highest_contiguous_nn, by = "LadlabID")

# hc.datawide <- right_join(hc.datawide, highest_contiguous_nn, by = "LadlabID")

# hc.datawide %>%
#   dplyr::select(LadlabID, Age, AgeGroup, productivity, max, 
#     HCReceivedSupport, ihc, dce, sup.noerror) %>%
#   group_by(productivity) %>%
#   summarize(median = median(max, na.rm=TRUE),
#             count = n())
# #median is 86 for all groups
```

Get mean WCN for everyone <span style="color:red">Not using this anymore - RMS</span>
```{r}
# lookup <- wcn.wide %>%
#   group_by(LadlabID)%>%
#   summarise(mean.NN = mean(immediate, na.rm = TRUE))
```

## Successor models
```{r}
#each participant only needs one row here, because we only need to know whether they are a Successor Knower or Endless Knower
distinct_model.df <- model.df %>%
  distinct(LadlabID, Age, AgeGroup, Gender, SuccessorKnower, EndlessKnower, 
           IHC, Highest_Contig_NN, FHC, DCE, Productivity, prod.gradient)%>%
  mutate(SuccessorKnower = factor(SuccessorKnower, levels = c(0,1)), 
         EndlessKnower = factor(EndlessKnower, levels = c(0,1)),
         IHC = as.integer(IHC), 
         Highest_Contig_NN = as.integer(Highest_Contig_NN), 
         LadlabID = factor(LadlabID), 
         IHC.c = as.vector(scale(IHC, center = TRUE, scale=TRUE)), #scale and center for model fit
         FHC.c = as.vector(scale(FHC, center = TRUE, scale=TRUE)),
         Highest_Contig_NN.c = as.vector(scale(Highest_Contig_NN, center = TRUE, scale=TRUE)), 
         Age.c = as.vector(scale(Age, center = TRUE, scale=TRUE)))

# #add mean_nn to model df
# distinct_model.df <- right_join(distinct_model.df, lookup, by = "LadlabID")

###MODEL BUILDING AND COMPARISONS###
#base model for successor knower
base.successor <- glm(SuccessorKnower ~ Age.c, family = "binomial", 
                        data = distinct_model.df)

##IHC model##
model.ihc.successor <- glm(SuccessorKnower ~ IHC.c + Age.c, family = "binomial", 
                             data = distinct_model.df)
##Highest NN Model##
model.nn.successor <- glm(SuccessorKnower ~ Highest_Contig_NN.c + Age.c, family = "binomial", 
                            data = distinct_model.df)
##Productivity model##
model.prod.successor <- glm(SuccessorKnower ~ Productivity + Age.c, family = "binomial",
                              data = distinct_model.df)

##EXPLORATORY## - GAIN SCORE
model.gain.successor <- glm(SuccessorKnower ~ prod.gradient + Age.c, family = "binomial",
                              data = distinct_model.df)
summary(model.gain.successor)

##Regression table for Successor Knower Models (Table 2)
mtable.sf.knowers <- mtable('Base' = base.successor,
            'IHC' = model.ihc.successor,
            'Highest Contig.' = model.nn.successor,
            'Productivity' = model.prod.successor,
            'Exp. - Prod. gain' = model.gain.successor,
            #summary.stats = c('R-squared','F','p','N'))
            summary.stats = c('Nagelkerke R-sq.','Log-likelihood','AIC','N'))
mtable.sf.knowers

###MODEL COMPARISONS##
#base v. IHC
anova(base.successor, model.ihc.successor, test = 'LRT') #IHC not significant

#Highest contiguous NN v. IHC
anova(base.successor, model.nn.successor, test = 'LRT')#highest contiguous NN not significant

#Productivity v. IHC
anova(base.successor, model.prod.successor, test = 'LRT')#Productivity trending


##Exploratory
anova(base.successor, model.gain.successor, test = 'LRT')
```


## Endless Models
```{r}
#Base model
base.endless <- glm(EndlessKnower ~ Age.c, family = "binomial", 
                      data = distinct_model.df)

###IHC MODEL###
model.ihc.endless <- glm(EndlessKnower ~ IHC.c + Age.c, family = "binomial", 
                           data = distinct_model.df)

###HIGHEST CONTIG NN MODEL###
model.nn.endless <- glm(EndlessKnower ~ Highest_Contig_NN.c + Age.c, family = "binomial", 
                          data = distinct_model.df) 

###PRODUCTIVITY MODEL###
model.prod.endless <- glm(EndlessKnower ~ Productivity + Age.c, family = "binomial", 
                            data = distinct_model.df)

##EXPLORATORY## - GAIN SCORE
model.gain.endless <- glm(EndlessKnower ~ prod.gradient + Age.c, family = "binomial", 
                          data = distinct_model.df)

##Regression table for Endless Models
mtable.endless.knowers <- mtable('Base' = base.endless,
            'IHC' = model.ihc.endless,
            'Highest Contig.' = model.nn.endless,
            'Productivity' = model.prod.endless,
            'Prod. gradient' = model.gain.endless,
            #summary.stats = c('R-squared','F','p','N'))
            summary.stats = c('Nagelkerke R-sq.','Log-likelihood','AIC','N'))

mtable.endless.knowers

##SIMPLE MODEL COMPARISONS##
#base v. IHC
anova(base.endless, model.ihc.endless, test = 'LRT') #IHC significant

#base v. highest contiguous
anova(model.nn.endless, base.endless, test = 'LRT')#Highest contig NN significant

#base v. productivity
anova(model.prod.endless, base.endless, test = 'LRT')#Prod significant

# #okay with about mean NN
# model2.endless <- glmer(EndlessKnower ~ mean.NN + Age + (1|LadlabID), family = "binomial", 
#                         data = distinct_model.df)
# anova(model2.endless, base.endless, test = 'LRT')#mean NN significant
```

### Endless: Large model comparison
Put all significant Endless predictors into large model, run model comparison

```{r}
##BASE MODEL WITH IHC
large.endless.base <- glm(EndlessKnower ~ IHC.c + Age.c, 
                            family = "binomial", data = distinct_model.df)
##add highest contig
large.endless.nn <- glm(EndlessKnower ~ Highest_Contig_NN.c + IHC.c + Age.c, 
                          family = "binomial", data = distinct_model.df)

##Productivity v. IHC##
large.endless.prod <- glm(EndlessKnower ~ Productivity + IHC.c + Age.c, 
                            family = "binomial", data = distinct_model.df)

##ALL THREE TOGETHER
large.endless.full <- glm(EndlessKnower ~ Productivity + Highest_Contig_NN.c + 
                              IHC.c + Age.c, 
                            family = "binomial", data = distinct_model.df)

#regression table
mtable.endless.large <- mtable('IHC alone' = large.endless.base,
            'Highest contiguous NN + IHC' = large.endless.nn,
            'Productivity + IHC' = large.endless.prod,
            'Prod. + Highest contig. + IHC' = large.endless.full,
            #summary.stats = c('R-squared','F','p','N'))
            summary.stats = c('Nagelkerke R-sq.','Log-likelihood','AIC','N'))

mtable.endless.large

##MODEL COMPARISONS
#IHC v. Highest contig.
anova(large.endless.base, large.endless.nn, test = 'LRT')#Highest contig. NS

#IHC v. Productivity
anova(large.endless.base, large.endless.prod, test = 'LRT')##Productivity NS

###########
##Exploratory - productivity gradient comparison
large.endless.gain <- glm(EndlessKnower ~ prod.gradient + Age.c, 
                          family = "binomial", data = distinct_model.df)
summary(large.endless.gain) #lower AIC than IHC, significant predictor
#add IHC to model
large.endless.gain.ihc <- glm(EndlessKnower ~ IHC.c + prod.gradient + Age.c, 
                              family = "binomial", data = distinct_model.df)
summary(large.endless.gain.ihc) #with addition of IHC, prod.gradient is marginal, AIC very slightly decreases, but addition of IHC does not significantly improve the fit of the model

anova(large.endless.gain, large.endless.gain.ihc, test = 'LRT')
```
 
#LM predicting IHC from productivity and age, HCNN and age
```{r}
lm.prod <- full.data %>%
  distinct(LadlabID, Productivity, Age, IHC)%>%
  mutate(Age.c = as.vector(scale(Age, center = TRUE, scale=TRUE)))

lm1 <- lm(IHC ~ Productivity + Age.c, data = lm.prod)
summary(lm1)


lm2 <- lm(IHC ~ Highest_Contig_NN + Age.c, data = distinct_model.df)
summary(lm2)
```

#Exploratory - what about with participants who did not reach 99?
```{r}
explore.dat <- distinct_model.df %>%
  filter(IHC < 99)

end.base <- glm(EndlessKnower ~ Age.c, family = "binomial", data = explore.dat)

#IHC
end.ihc <- glm(EndlessKnower ~ IHC.c + Age.c, family = "binomial", data = explore.dat)
end.prod <- glm(EndlessKnower ~ Productivity + Age.c, family = "binomial", data = explore.dat)
end.nn <- glm(EndlessKnower ~Highest_Contig_NN + Age.c, family = "binomial", data = explore.dat)
```

#Exploratory - trying to account for distance between IHC and FHC
```{r}
tmp <- distinct_model.df %>%
  mutate(delta.hc = FHC-IHC)%>%
  mutate(prop.hc = delta.hc/(100-IHC), 
         prop.hc = ifelse(prop.hc == "NaN", 1, as.numeric(prop.hc)), 
         prop.hc = ifelse(prop.hc == 0 & IHC == 99, 1, as.numeric(prop.hc))) #one kid with IHC and FHC as 99

#plot by IHC
ggplot(full.data, aes(x = prod.gradient, y = IHC, colour = Productivity)) +
  geom_point(size = 3, alpha = .1)+
  geom_jitter()+
  theme_bw(base_size = 13) +
  theme(legend.position = "bottom") +
  scale_y_continuous(breaks = seq(0, 100, 10)) +
  scale_colour_brewer(palette = "Set1") + 
  labs(x = 'Productivity Gradient', y = 'IHC')

end.gain.ihc <- glm(EndlessKnower ~ IHC.c + Age.c, family = "binomial", 
                data = distinct_model.df)
end.gain.Prod <- glm(EndlessKnower ~ Productivity + Age.c, family = "binomial", 
                     data = distinct_model.df)
end.gain.gain <- glm(EndlessKnower ~ gain.hc + Age.c, family = "binomial", 
                     data = distinct_model.df)
end.gain.nn <- glm(EndlessKnower ~ Highest_Contig_NN + Age.c, 
                   family = "binomial", data = distinct_model.df)
summary(end.gain.ihc)
summary(end.gain.Prod)
summary(end.gain.gain)
summary(end.gain.nn)

#add IHC to model with gain score
end.gain.ihcgain <- glm(EndlessKnower ~ IHC.c + gain.hc + Age.c, family = "binomial", 
                        data = distinct_model.df)
anova(end.gain.ihcgain, end.gain.gain, test = 'LRT')

#correlation between productivity and gain score
tmp %<>%
  mutate(Prod.num = ifelse(Productivity == "Productive", 1, 0))

cor.test(tmp$Prod.num, tmp$prop.hc)
```

#Plot of prod. gain with IHC - WIP
```{r}
# pg.ms <- full.data %>%
#   distinct(LadlabID, IHC, FHC, prod.gradient, Productivity)
# 
# ggplot(pg.ms, aes(x=IHC, y = prod.gradient, colour = Productivity)) +
#   geom_point(size = 2) +
#   scale_x_continuous(breaks = seq(0, 100, 10)) +
#   scale_colour_brewer(palette = "Set1") +
#   theme_bw(base_size = 13) +
#   theme(panel.grid.minor = element_blank(), 
#         legend.position = "bottom", 
#         legend.title =  element_blank())

ms <- hc.dev.data %>%
  filter(Productivity == "Productive")


hc.dev.data %>%
  filter(Productivity == "Productive")%>%
  filter(`Highest Count Coding` != "DCE")%>%
ggplot(aes(x = reorder(LadlabID, hc, FUN=min), y = hc, colour = prod.gradient)) + 
  geom_point(aes(shape = `Highest Count Coding`), 
             size = 1.2, stroke = 1.2) +
  geom_line() + 
  # scale_color_brewer(palette="Dark2") +
  scale_shape_manual(values = c(5, 20)) +
  scale_y_continuous(breaks = seq(0, 140, 10)) +
  labs(x = "Each line = individual participant",
       y="Highest Count") +
  theme_bw() + 
  theme(legend.position="bottom", 
        axis.text.x = element_text(angle = 270, hjust = 1)) + 
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), 
        panel.grid.minor = element_blank(), 
        panel.grid.major = element_blank()) +
  # scale_colour_gradient(low = "#666666",
  #                       high = "#00b8e6") +
  labs(shape = "Highest Count Type", colour = "Productivity Gradient")


ggplot(ms, aes(x = reorder(LadlabID, hc, FUN=min), y = hc)) + 
  facet_grid(rows = vars(Productivity)) +
  geom_line(data=hc.dev.prod[!is.na(hc.dev.prod$hc) + 
  geom_point(aes(shape = `Highest Count Coding`, colour = `Highest Count Coding`), 
             size = 2, stroke = 1.5) +
  scale_color_brewer(palette="Dark2") +
  scale_shape_manual(values = c(4,5,20)) +
  ylim(0, 100) +
  labs(x = "Each line = individual participant",
       y="Highest Count") +
  theme_bw(base_size = 13) + 
  theme(legend.position="bottom", 
        axis.text.x = element_text(angle = 270, hjust = 1)) + 
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
ggsave('graphs/distance-prod-sorted.png')

#nonproductive
ggplot(hc.dev.nonprod, aes(x = reorder(LadlabID, hc, FUN=min), y = hc)) + 
  facet_grid(rows = vars(Productivity)) +
  geom_line(data=hc.dev.nonprod[!is.na(hc.dev.nonprod$hc),]) + 
  geom_point(aes(shape = `Highest Count Coding`, colour = `Highest Count Coding`), 
             size = 2, stroke = 1.5) +
  scale_color_brewer(palette="Dark2") +
  scale_shape_manual(values = c(4,5,20)) +
  ylim(0, 100) +
  labs(x = "Each line = individual participant",
       y="Highest Count") +
  theme_bw(base_size = 13) + 
  theme(legend.position="bottom", 
        axis.text.x = element_text(angle = 270, hjust = 1)) +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
ggsave('graphs/distance-nonprod-sorted.png')
```