---
title: "RecursionAnalysis"
author: "Junyi Chu, Rose M. Schneider, Pierina Cheung"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_depth: 4
    keep_md: true
---

# Setup
```{r setup, include=FALSE}
rm(list = ls())
require("knitr")

# # Set WD
 opts_knit$set(root.dir = "~/Sites/recursion/")
#opts_knit$set(root.dir = "~/Projects/Junyi study/recursiongithub/") #for PC
#opts_knit$set(root.dir = "~/Documents/Projects/recursion/") #this is specific to RMS, change accordinglyz

# For wrapping lines when knitting
opts_chunk$set(tidy.opts=list(width.cutoff=80),tidy=TRUE,
               warning=FALSE)

library(Hmisc)
library(tidyverse)
library(magrittr)
#library(langcog)
library(lme4)
library(stringr)
library(RColorBrewer)
library(ggthemes)
library(memisc)
library(broom)
library(sjPlot)
# Set seed for reproducible analyses
set.seed(43)
'%!in%' <- function(x,y)!('%in%'(x,y))

# colors
prod.pal <- c("#E41A1C", "#4DAF4A", "#377EB8")

# cb friendly red blue green
mypalette <- c("#D55E00", "#0073B3", "#009E73")

# cb friendly green, orange, bright blue for fig3
mypalette3 <- c("#009E73", "#E69F00", "#56B4E9")
```

R Version for citation is: `r R.version.string`.

## Loading data
```{r}
#original data
full.data <- read.csv('data/recursion_full.csv', na.strings=c(""," ","NA", "NA "))
```

Reasons for exclusion and their numbers
```{r}
full.data %>%
  dplyr::filter(ExclusionGroup != "include") %>%
  dplyr::distinct(LadlabID, .keep_all = TRUE) %>%
  dplyr::group_by(ExclusionGroup) %>%
  dplyr::summarize(countN = dplyr::n_distinct(LadlabID)) %>%
  kable()
```


RMS original code for checking who failed practice - do not need to run. EVAL set to FALSE
```{r eval = FALSE}

# check how many failed both practice trials
x <- full.data %>%
  filter(Task == "WCN" &
           (TaskItem == 1 | TaskItem == 5))%>%
  group_by(LadlabID)%>%
  summarise(sum = sum(Accuracy))%>%
  filter(sum != 3)

#just hardcoding kids because it's easier than going back to the full data frame
#These kids got 1 right, 5 wrong: 
one.corr <- as.vector(c("013316-BO", "033616-JM", "030316-ED", 
                        "030817-ZI", "031516-A", "033316-JH", 
                        "033316-RC", "040317-AL", "040317-SL", 
                        "041316-AR", "041316-NC", "041316-VN", 
                        "063416-MC"))

five.corr <- as.vector("050617-Z1")

zero.corr <- as.vector(c("030316-AD", "040616-K"))


```

Exclude those who failed the practice trials on What Comes Next Task
```{r}

#final decision: remove kids who fail 1 trial out of 3 trials, with no additional information about whether E reran the failed trial. Removing 8 kids in total

# added 033516-ML on 3018-09-03 to the exclusion list. kid had NA data for wcn practice trials and 0 correct on test. assume kid failed wcn.

full.data %<>%
  mutate(ExclusionGroup = ifelse(LadlabID == "033616-JM"| LadlabID == "030316-AD"|
                                   LadlabID == "031516-A" | LadlabID == "041316-AR"|
                                   LadlabID == "041316-VN" | LadlabID == "033316-RC"|
                                   LadlabID == "013316-BO"| LadlabID == "041316-NC"|
                                   LadlabID == "033516-ML", "fail wcn", levels(ExclusionGroup)[ExclusionGroup]),
         ExclusionGroup = as.factor(ExclusionGroup))

# check. good
# full.data %>%
#   filter(LadlabID == "033616-JM")

```

Let's remove anyone who should not be included in the final dataset.
```{r}
full.data %<>%
  dplyr::filter(ExclusionGroup == "include")

```


Now, add in the Productivity classification, IHC, and FHC from PC, JC, and RMS coding

```{r}
#productivity, fhc, ihc coding from pc, jc, and rms
hc.data <- read.csv('data/HC-datawide-forcoding - hc.datawide.csv') %>%
  dplyr::select(LadlabID, prod_tomerge, ihc_tomerge, fhc_tomerge, dce, why_productive, sup.times)

full.data <- dplyr::left_join(full.data, hc.data, by = "LadlabID")

full.data %<>%
  dplyr::rename(Productivity = prod_tomerge, 
                IHC = ihc_tomerge, 
                FHC = fhc_tomerge, 
                DCE = dce)%>%
  dplyr::mutate(Productivity = factor(Productivity, levels = c("nonprod", "prod"), 
                                      labels = c("Nonproductive", "Productive")), 
                IHC = ifelse(IHC > 100, 100, IHC),
                FHC = ifelse(FHC > 100, 100, FHC)) %>%
    mutate(Productivity.tertiary = ifelse(IHC >= 99, "Productive (IHC \u3365 99)", 
                             ifelse(Productivity == "Productive", "Productive (IHC < 99)", "Nonproductive")))


#do a quick check to make sure we have the same SIDs in each
unique.full <- as.vector(unique(full.data$LadlabID))
unique.hc <- as.vector(unique(hc.data$LadlabID))

tmp <- hc.data %>%
  dplyr::filter(LadlabID %!in% unique.full)

#good to go - the only kids who are not included in full data are the ones who we excluded
```

Add in coding for reminder prompts and recovery from reminders
```{r}
reminders.data <- read.csv('data/sara-HC-datawide-forcoding - hc.datawide.csv') %>%
  dplyr::select(LadlabID, reminders.total, reminders.recovered)
full.data <- dplyr::left_join(full.data, reminders.data, by="LadlabID")
```

## Post-exclusion summary
Number of kids by age group and average age
```{r}
full.data %>%
  dplyr::group_by(AgeGroup) %>%
  dplyr::summarize(sumAge = n_distinct(LadlabID)) %>%
  kable()

full.data %>%
  dplyr::distinct(LadlabID, .keep_all = TRUE) %>%
  dplyr::summarize(minAge = min(Age),
                   maxAge = max(Age),
                   meanAge = mean(Age),
                   sdAge = sd(Age)) %>%
  kable(digits=3)
```

Number of kids who were classified as decade productive & nonproductive
```{r}
full.data %>%
  dplyr::distinct(LadlabID, Productivity, Age)%>%
  dplyr::group_by(Productivity)%>%
  dplyr::summarise(n = n(),
                   meanage = mean(Age, na.rm=TRUE),
                   sdage = sd(Age, na.rm=TRUE),
                   minage = min(Age, na.rm=TRUE),
                   maxage = max(Age, na.rm=TRUE)) %>%
  kable(digits=3)
```

Number of kids for the 3-way productivity classification
```{r}
full.data %>%
  dplyr::distinct(LadlabID, Productivity.tertiary, Age)%>%
  dplyr::group_by(Productivity.tertiary)%>%
  dplyr::summarise(n = n(),
                   meanage = mean(Age, na.rm=TRUE),
                   sdage = sd(Age, na.rm=TRUE),
                   minage = min(Age, na.rm=TRUE),
                   maxage = max(Age, na.rm=TRUE)) %>%
  kable(digits=3)
```

Reasons for productivity classification
```{r}
full.data %>%
  dplyr::distinct(LadlabID, Productivity.tertiary, why_productive)%>%
  dplyr::group_by(Productivity.tertiary, why_productive) %>%
  tally() %>%
  spread(Productivity.tertiary, n)
```


Just for reference, this is the number of kids who switched classifications from PC, JC, RMS recode
```{r}
full.data %>%
  dplyr::filter(TaskType == "productivity") %>%
  droplevels()%>%
  dplyr::distinct(LadlabID, Response, Productivity) %>%
  dplyr::mutate(Response = factor(Response, levels = c("nonprod", "prod"),
                         labels = c("Nonproductive", "Productive")))%>%
  dplyr::mutate(changed_classification = ifelse((is.na(Response) & Productivity == "Nonproductive"),
                                                "NA_toNonprod",
                                                ifelse((is.na(Response) & Productivity == "Productive"), 
                                                       "NA_toProd", 
                                                       ifelse((Response == "Nonproductive" & Productivity == "Productive"), 
                                                              "Nonprod_toProd", 
                                                              ifelse((Response == "Productive" & Productivity == "Nonproductive"),
                                                                     "Prod_toNonprod", "no_change")))))%>%
  dplyr::group_by(changed_classification)%>%
  dplyr::summarise(n =n())
```

## Calculate Productivity gradient
```{r}
full.data %<>%
  mutate(delta.hc = FHC-IHC, 
         prod.gradient = delta.hc/(99-IHC), 
         prod.gradient = ifelse(IHC >= 99, 1, as.numeric(prod.gradient)), 
         prod.gradient = ifelse(prod.gradient == 0 & IHC == 99, 1, as.numeric(prod.gradient)))
```

***
# Highest Count Descriptives

## Summary descriptives 
Average of IHC, DCE, and FHC for all kids
```{r}
full.data %>%
  dplyr::distinct(LadlabID, IHC, DCE, FHC, delta.hc, prod.gradient, sup.times)%>%
  dplyr::summarise_at(c('IHC','DCE','FHC',
                        'delta.hc', 'prod.gradient',
                        'sup.times'),
                      list(~mean(., na.rm=T), 
                           ~sd(., na.rm=T),
                           ~min(., na.rm=T),
                           ~max(., na.rm=T),
                           ~sum(!is.na(.)))) %>%
  gather(stat, val) %>%
  separate(stat, into = c("var", "stat"), sep = "_") %>%
  spread(stat, val) %>%
  dplyr::select(var, n=sum, mean, sd, min, max) %>%
  kable(digits=3)
```

Similar data by decade productivity
```{r}
full.data %>%
  dplyr::distinct(LadlabID, Productivity, IHC, DCE, FHC, delta.hc, prod.gradient, sup.times)%>%
  group_by(Productivity) %>%
  dplyr::summarise_at(c('IHC','DCE','FHC',
                        'delta.hc', 'prod.gradient',
                        'sup.times'),
                      list(~mean(., na.rm=T), 
                           ~sd(., na.rm=T),
                           ~min(., na.rm=T),
                           ~max(., na.rm=T),
                           ~sum(!is.na(.)))) %>%
  gather(stat, val, -Productivity) %>%
  separate(stat, into = c("var", "stat"), sep = "_") %>%
  spread(stat, val) %>%
  dplyr::select(Productivity, var, n=sum, mean, sd, min, max) %>%
  kable(digits=3)
```

Again by 3-way decade productivity
```{r}
full.data %>%
  dplyr::distinct(LadlabID, Productivity.tertiary, IHC, DCE, FHC, delta.hc, prod.gradient, sup.times)%>%
  group_by(Productivity.tertiary) %>%
  dplyr::summarise_at(c('IHC','DCE','FHC',
                        'delta.hc', 'prod.gradient',
                        'sup.times'),
                      list(~mean(., na.rm=T), 
                           ~sd(., na.rm=T),
                           ~min(., na.rm=T),
                           ~max(., na.rm=T),
                           ~sum(!is.na(.)))) %>%
  gather(stat, val, -Productivity.tertiary) %>%
  separate(stat, into = c("var", "stat"), sep = "_") %>%
  spread(stat, val) %>%
  dplyr::select(Productivity.tertiary, var, n=sum, mean, sd, min, max) %>%
  kable(digits=3)
```

## Histogram

### Fig 1

Plotting distribution of IHC, as a function of productivity (~ junyi's graph)

```{r echo=FALSE}
unique.hc.data <- full.data %>%
  dplyr::distinct(LadlabID, Gender, Age, AgeGroup, HCReceivedSupport, IHC, DCE, FHC, Productivity, Productivity.tertiary)

ggplot(unique.hc.data, aes(x=IHC, color=Productivity)) + 
  geom_dotplot(aes(fill = Productivity),
               binwidth=1, stackgroups=TRUE, binpositions="all",method="dotdensity", dotsize = 1) +
  scale_color_manual(values=c("#D55E00", "#0073B3", "#009E73")) + 
  scale_fill_manual(values=c("#D55E00", "#0073B3", "#009E73")) +
  coord_fixed(ratio=1) +
  scale_y_continuous(breaks=seq(0,40,10), lim=c(0,35)) +
  scale_x_continuous(breaks=seq(0,100,by=10)) +
  labs(x="IHC", 
       y="Frequency") +
  theme_bw(base_size = 11) + 
  theme(legend.position="bottom", 
        legend.title = element_blank(), 
        panel.grid.minor = element_blank())
ggsave('graphs/ihc-by-prod.png')

## three-way productivity
ggplot(unique.hc.data, aes(x=IHC, color=Productivity.tertiary)) + 
  geom_dotplot(aes(fill = Productivity.tertiary),
               binwidth=1, stackgroups=TRUE, binpositions="all",method="dotdensity", dotsize = 1) +
  scale_color_manual(values=mypalette, name="Productivity") + 
  scale_fill_manual(values=mypalette, name="Productivity") +
  coord_fixed(ratio=1) +
  scale_y_continuous(breaks=seq(0,40,10), lim=c(0,35)) +
  scale_x_continuous(breaks=seq(0,100,by=10)) +
  labs(x="IHC", 
       y="Frequency") +
  theme_bw(base_size = 11) + 
  theme(legend.position="bottom", 
        legend.title = element_blank(), 
        panel.grid.minor = element_blank())
ggsave('graphs/ihc-by-prod3.png')

## Black graph for talk purposes
ggplot(unique.hc.data, aes(x=IHC)) + 
  geom_dotplot(binwidth=1, stackgroups=TRUE, binpositions="all",method="dotdensity", dotsize = 1) +
  coord_fixed(ratio=1) +
  scale_y_continuous(breaks=seq(0,40,10), lim=c(0,35)) +
  scale_x_continuous(breaks=seq(0,100,by=10)) +
  labs(x="IHC", 
       y="Frequency") +
  theme_bw(base_size = 11) + 
  theme(legend.position="bottom", 
        legend.title = element_blank(), 
        panel.grid.minor = element_blank())
ggsave('graphs/ihc.png')
```

### by age
Plotting productivity as a function of age in months

```{r echo=FALSE}
unique.hc.data$AgeMonths = floor(unique.hc.data$Age*13)

ggplot(unique.hc.data, aes(x=AgeMonths, colour = Productivity)) + 
  geom_dotplot(aes(fill = Productivity),
               binwidth = 1,
               stackgroups=TRUE, binpositions="all") +
  coord_fixed(ratio=1) +
  scale_y_continuous(breaks=seq(0,10,5), lim=c(0,13)) +
  scale_x_continuous(breaks=seq(48,73,by=6)) +
  scale_color_manual(values=c("#D55E00", "#0073B3", "#009E73")) + 
  scale_fill_manual(values=c("#D55E00", "#0073B3", "#009E73")) +
  labs( x="Age in Months", 
       y="Frequency") +
  theme_bw(base_size = 11) + 
  theme(legend.position="right",
        legend.title = element_blank())
ggsave('graphs/prod-by-age.png')

ggplot(unique.hc.data, aes(x=AgeMonths, colour = Productivity.tertiary)) + 
  geom_dotplot(aes(fill = Productivity.tertiary),
               binwidth = 1,
               stackgroups=TRUE, binpositions="all") +
  coord_fixed(ratio=1) +
  scale_y_continuous(breaks=seq(0,10,5), lim=c(0,13)) +
  scale_x_continuous(breaks=seq(48,73,by=6)) +
  scale_color_manual(values=mypalette) + 
  scale_fill_manual(values=mypalette) +
  labs( x="Age in Months", 
       y="Frequency") +
  theme_bw(base_size = 11) + 
  theme(legend.position="right",
        legend.title = element_blank())
ggsave('graphs/prod-by-age-3.png',
       width=6, height=3)
```

## Distance between IHC and FHC

Restructure data to plot distance between IHC, DCE, and FHC
```{r}
hc.dev.data <- full.data %>%
  dplyr::select(LadlabID, Age, Productivity, IHC, DCE, FHC, prod.gradient) %>%
  gather(hcprogression, hc, IHC:FHC)%>%
  mutate(hcprogression = factor(hcprogression, levels = c("IHC", "DCE", "FHC"))) %>%
  dplyr::rename(`Highest Count Coding` = hcprogression)

hc.dev.prod <- subset(hc.dev.data, Productivity == "Productive")
hc.dev.nonprod <- subset(hc.dev.data, Productivity == "Nonproductive")
```

### Fig 3a/b
Separate graphs for productivity groups, sorted by ascending IHC
```{r echo=FALSE}
#productive
ggplot(hc.dev.prod, aes(x = reorder(LadlabID, hc, FUN=min), y = hc)) + 
  facet_grid(rows = vars(Productivity)) +
  geom_line(data=hc.dev.prod[!is.na(hc.dev.prod$hc),]) + 
  geom_point(aes(shape = `Highest Count Coding`, colour = `Highest Count Coding`), 
             size = 3, stroke = 1.5) +
  scale_color_brewer(palette = "Dark3", labels=c("Initial Highest Count", "Decade-Change Error", "Final Highest Count")) +
  scale_shape_manual(values = c(4,5,30), labels=c("Initial Highest Count", "Decade-Change Error", "Final Highest Count")) +
  ylim(0, 100) +
  labs(title="a. Distance, Productive Counters",
       x = "Each line = individual participant",
       y="Highest Count",
       colour="Highest Count Coding",
       shape="Highest Count Coding") +
  theme_bw(base_size = 13) + 
  theme(legend.position="bottom", 
        #axis.text.x = element_text(angle = 370, hjust = 1),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
ggsave('graphs/distance-prod-sorted.png', width=8, height=4)

#nonproductive
ggplot(hc.dev.nonprod, aes(x = reorder(LadlabID, hc, FUN=min), y = hc)) + 
  facet_grid(rows = vars(Productivity)) +
  geom_line(data=hc.dev.nonprod[!is.na(hc.dev.nonprod$hc),]) + 
  geom_point(aes(shape = `Highest Count Coding`, colour = `Highest Count Coding`), 
             size = 3, stroke = 1.5) +
  scale_color_brewer(palette = "Dark3", labels=c("Initial Highest Count", "Decade-Change Error", "Final Highest Count")) +
  scale_shape_manual(values = c(4,5,30), labels=c("Initial Highest Count", "Decade-Change Error", "Final Highest Count")) +
  ylim(0, 100) +
  labs(title="b. Distance, Non-productive Counters",
       x = "Each line = individual participant",
       y="Highest Count",
       colour="Highest Count Coding",
       shape="Highest Count Coding") +
  theme_bw(base_size = 13) + 
  theme(legend.position="bottom", 
        #axis.text.x = element_text(angle = 370, hjust = 1),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) 
ggsave('graphs/distance-nonprod-sorted.png', width=8, height=4)

```

Number of kids who counted to 99+ spontaneously on IHC plus those whose FHC = 99+ without prompting
```{r}
# full.data %>%
#   filter(IHC > 98) %>%
#   distinct(LadlabID, IHC, FHC, HCReceivedSupport) %>%
#   count() #n=33
# but some kids made errors past IHC but < 3 so need to account for that
full.data %>%
  filter(FHC > 98 & (is.na(HCReceivedSupport)|HCReceivedSupport != 1)) %>%
  distinct(LadlabID, IHC, FHC, HCReceivedSupport) %>%
  count() #n =43

```

## Decade prompts

Check coding sheet against 'supported.times' coding. Print conflicts. Use "sup.times" instead.
- 030116-PW & 041416-BF: Experimenter should not have provided prompts, multiple errors before first DCE
- 063416-MC: Experimenter's prompts are 100 and 110, should not count.
```{r}
full.data %>%
  filter(TaskItem=="times") %>%
  distinct(LadlabID, HCReceivedSupport, TaskItem, Response, sup.times, Productivity) %>%
  mutate(Response = as.integer(levels(Response)[Response])) %>%
  filter(is.na(sup.times) & !is.na(Response) | 
           is.na(Response) & !is.na(sup.times) |
           sup.times > Response |
           sup.times < Response) %>%
  kable()
```

Average number of decade prompts provided. Productive counters first. Analyze from raw data:
```{r}
full.data %>%
  distinct(LadlabID, sup.times, Productivity, Productivity.tertiary) %>%
  group_by(Productivity.tertiary) %>% 
  summarize(n=n(),
            n.sup=sum(sup.times>0, na.rm=T),
            mean = mean(sup.times, na.rm=TRUE),
            sd = sd(sup.times, na.rm=TRUE),
            min = min(sup.times, na.rm=TRUE),
            max = max(sup.times, na.rm=TRUE)) %>%
  kable(digits=3)

# assume 0 = NA
# error in supported.times coding, should only count to 90
# but one kid got prompted with 100 and 110 and times should be 0
```

## Reminder prompts
How many kids have coded data for receiving reminders?
```{r}
full.data %>%
  dplyr::select(LadlabID, Productivity, reminders.total, reminders.recovered) %>%
  unique()%>%
  na.omit() %>%
  summarise(Ncoded=n(), 
            total.min=min(reminders.total),
            total.max=max(reminders.total),
            total.mean=mean(reminders.total),
            total.median=median(reminders.total))
```

How often did kids miss a reminder? Remember that the experiment ended when kids failed to recover from a reminder, unless that failure occured at a decade transition in which case the experimenter would provide a decade prompt and continue the experiment. 
```{r}
full.data %>%
  dplyr::select(LadlabID, Productivity, reminders.total, reminders.recovered) %>%
  unique()%>%
  na.omit() %>%
  mutate(missed = reminders.total-reminders.recovered) %>%
  summarise(Ncoded=n(), 
            missed.min=min(missed),
            missed.max=max(missed),
            missed.mean=mean(missed),
            missed.median=median(missed)) %>%
  kable(digits=3)
# look at proportion of kids who failed to recover from reminders.
full.data %>%
  dplyr::select(LadlabID, Productivity, reminders.total, reminders.recovered) %>%
  unique()%>%
  na.omit() %>%
  mutate(missed = reminders.total-reminders.recovered) %>%
  group_by(reminders.total) %>%
  summarise(Nkids=n(),N.kids.missed=sum(missed),Perc.kids.missed=sum(missed)/n()) %>%
  kable(digits=3)
```


# What Comes Next Descriptives

First check if Accuracy column in full.data is coded correctly. Good to go.
```{r}
wcn.data <- full.data %>%
  filter(Task == "WCN")

wcn.data %<>%
  mutate(Response_num = as.numeric(as.character(Response)), 
         TaskItem_num = as.numeric(as.character(TaskItem)), 
         Accuracy_check = ifelse(Response_num == (TaskItem_num + 1), 1, 0), 
         Accuracy_valid = ifelse(Accuracy == Accuracy_check, TRUE, FALSE))

validate <- function(){
  validation <- wcn.data %>%
    filter(Accuracy_valid == FALSE)
  if(length(validation$LadlabID) > 0) {
    print("WARNING: CHECK CODING")
  } else {
    print("All coding correct")
  }
}

validate()
```

Add overall accuracy to the dataframe.
```{r}
wcn.accuracy <- wcn.data %>% 
    filter(TaskType != "practice") %>%
  filter(TaskType == "immediate") %>%
  group_by(LadlabID) %>%
  mutate(wcnscore=sum(Accuracy, na.rm = TRUE)) %>%
  dplyr::select(LadlabID, wcnscore) %>%
  unique()

wcn.data <- left_join(wcn.data, wcn.accuracy, by="LadlabID")
```

Immediate vs. Momentum trials: Children were provided with momentum trials if they got wrong on immediate trials. Check %trials where immediate = wrong, momentum = right
```{r}
wcn.wide <- wcn.data %>%
  filter(TaskType != "practice") %>%
  filter(TaskItem != 3) %>% # a trial on 3 for momentum that doesn't exist for immediate
  droplevels()%>%
  dplyr::select(LadlabID, Age, AgeGroup, TaskType, TaskItem, Accuracy, Productivity, prod.gradient) %>%
  spread(TaskType, Accuracy)

# data check: some kids got 1 for immediate but 0 for momentum or 1 for immediate and 1 for momentum (N = 5).Keeping them. 
## for reference, pulling out these kids below
full.data %>%
  filter(Task == "WCN", 
         TaskType == "momentum" | TaskType == "immediate")%>%
  dplyr::select(LadlabID, Age, AgeGroup, TaskType, TaskItem, Accuracy) %>%
  spread(TaskType, Accuracy)%>%
  mutate(issue_immediate1Momentum0 = ifelse(immediate == 1 & momentum == 0, TRUE, FALSE), 
         issue_immediate1Momentum1 = ifelse(immediate == 1 & momentum == 1, TRUE, FALSE))%>%
  filter(issue_immediate1Momentum0 == TRUE | 
           issue_immediate1Momentum1 == TRUE)

# how many kids show improved performance
xtabs(~immediate + momentum, data = wcn.wide, na.action = na.pass, exclude = NULL)
# 191 / 1048 trials = ~ 18%. NOTE % not by kids but by trials.
```

## Percent Correct on WCN 
```{r}
wcn.data %>%
  dplyr::distinct(LadlabID, wcnscore)%>%
  dplyr::summarise(n=n(),
                   avg.wcn = mean(wcnscore)/8,
                   sd.wcn = sd(wcnscore)/8) %>%
  kable(digits=3)

# Productivity
wcn.data %>%
  dplyr::distinct(LadlabID, Productivity, wcnscore)%>%
  group_by(Productivity) %>%
  dplyr::summarise(n=n(),avg.wcn = mean(wcnscore)/8,
                   sd.wcn = sd(wcnscore)/8) %>%
  kable(digits=3)

# Productivity 3-ways
wcn.data %>%
  dplyr::distinct(LadlabID, Productivity.tertiary, wcnscore)%>%
  group_by(Productivity.tertiary) %>%
  dplyr::summarise(n=n(),avg.wcn = mean(wcnscore)/8,
                   sd.wcn = sd(wcnscore)/8) %>%
  kable(digits=3)
```

T-test
```{r}
wcn.data %>%
  dplyr::distinct(LadlabID, Productivity, wcnscore)%>%
  t.test(wcnscore ~ Productivity, data=.)
```


Plotting %corr on WCN as function of productivity
```{r}
wcn.data %>%
  dplyr::filter(TaskType == "immediate") %>%
  dplyr::group_by(LadlabID, Productivity, prod.gradient) %>%
  dplyr::summarize(avg.wcn = mean(Accuracy, na.rm=TRUE),
                   sd.wcn = sd(Accuracy, na.rm=TRUE)) %>%
  ggplot(aes(x = Productivity, y = avg.wcn, fill=factor(Productivity))) +
  stat_summary(fun.y = mean, position = position_dodge(width = .95), 
               geom="bar", alpha = .8, colour = "black") +
  geom_violin(alpha = .3) +
  stat_summary(fun.data = mean_se, geom="errorbar", 
               position = position_dodge(width=0.90), width = 0.3)+
  #scale_fill_discrete(name = "Productivity") +
  scale_fill_manual(name = "Productivity", values = mypalette, guide = "none") +
  scale_colour_brewer(palette = "Greys") +
  ylab("Proportion Correct") + 
  xlab('Productivity') + 
  theme_bw(base_size = 13) + 
  theme(legend.position = "none", 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  theme(text = element_text(size = 13)) +
  ylim(0, 1.0) 
  
ggsave('graphs/wcn-percentcorr.png')


```

### Fig 3
Jess graph
```{r fig3}
fig3.data <- wcn.data %>%
  filter(TaskType == "immediate")%>%
  mutate(TaskItem_type= ifelse(mod(TaskItem_num,10)==9, "Decade transition", "Mid-decade")) %>%
  mutate(TaskItem_type_ordered = ordered(TaskItem_type, levels=c("Mid-decade", "Decade transition")))

fig3.data %>%
  group_by(TaskItem_type_ordered, TaskItem, Productivity.tertiary)%>%
   summarise(mean = mean(Accuracy, na.rm = TRUE), 
            n = n(), 
            sd = sd(Accuracy, na.rm = TRUE), 
            se = sd/sqrt(n)) %>%
  ggplot(aes(x = factor(TaskItem), y = mean, colour = Productivity.tertiary, group= Productivity.tertiary)) +
  geom_point(size = 3.5) + 
  geom_line(size = .7) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), 
                width = 0, size = .5) +
  facet_grid(~TaskItem_type_ordered, scales = "free_x") +#, space = "free_x") +
  theme_bw(base_size = 13) + 
  scale_colour_manual(values = mypalette) +
  theme(legend.position = "right", legend.title = element_blank()) +
  labs(x = "Task item", y = "Mean performance") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
        #, strip.text=element_text(margin=margin(t=5, b=5, l=30, r=30)))
ggsave('graphs/wcn-trial-accuracy.png',
       width=7, height=4)
```

Get summary statistics by productivity and item type
```{r, echo=FALSE}
fig3.df <- fig3.data %>%
#  filter(Productivity.tertiary != "Productive (IHC \u3365 99)") %>%
  dplyr::select(c(LadlabID, IHC, FHC, Age, Productivity.tertiary,
                  TaskItem_num, TaskItem_type, Accuracy)) %>%
  mutate(IHC = as.integer(IHC),
         LadlabID=as.factor(LadlabID),
         TaskItem_type=as.factor(TaskItem_type))

# means by item type
fig3.df %>%
  group_by(LadlabID, TaskItem_type) %>%
  summarise(score=mean(Accuracy, na.rm=T)) %>%
  ungroup() %>%
  group_by(TaskItem_type) %>%
  summarise(mean=mean(score, na.rm=T), sd=sd(score, na.rm=T), n=n()) %>%
  kable(digits=3)
# means by productivity
fig3.df %>%
  group_by(LadlabID, Productivity.tertiary) %>%
  summarise(score=mean(Accuracy, na.rm=T)) %>%
  ungroup() %>%
  group_by(Productivity.tertiary) %>%
  summarise(mean=mean(score, na.rm=T), sd=sd(score, na.rm=T), n=n())%>%
  kable(digits=3)
# means by productivity and item type
fig3.df %>%
  group_by(LadlabID, Productivity.tertiary, TaskItem_type) %>%
  summarise(score=mean(Accuracy, na.rm=T)) %>%
  ungroup() %>%
  group_by(Productivity.tertiary, TaskItem_type) %>%
  summarise(mean=mean(score, na.rm=T), sd=sd(score, na.rm=T), n=n())%>%
  kable(digits=3)
```

### Productive (IHC<99) vs. Nonproductive on NN accuracy

Build dataframe and mean-center IHC, FHC and age.
```{r, echo=FALSE}
# Only for productive IHC < 99 and nonproductive
fig3.modelA.df <- fig3.data %>%
  filter(Productivity.tertiary != "Productive (IHC \u3365 99)") %>%
  dplyr::select(c(LadlabID, IHC, FHC, Age, Productivity.tertiary,
                  TaskItem_num, TaskItem_type, Accuracy)) %>%
  mutate(Productivity.tertiary=as.factor(Productivity.tertiary),
         IHC = as.integer(IHC),
         LadlabID=as.factor(LadlabID),
         TaskItem_type=as.factor(TaskItem_type)) %>%
  mutate(IHC.c = as.vector(scale(IHC, center = TRUE, scale=TRUE)), #scale and center for model fit
         FHC.c = as.vector(scale(FHC, center = TRUE, scale=TRUE)), 
         age.c = as.vector(scale(Age, center = TRUE, scale=TRUE)))
str(fig3.modelA.df)
```

Regression testing for interaction of productivity and decade/non-decade item type on WCN accuracy
```{r}
##WCN model looking at interaction between productivity and decade/non-decade item accuracy
fig3.modelA.prod <- glmer(Accuracy ~ Productivity.tertiary + IHC.c + age.c + 
                            (1|TaskItem_num) + (1|LadlabID), 
                          family = "binomial", data = fig3.modelA.df)
fig3.modelA.itemtype <- glmer(Accuracy ~ TaskItem_type +
                                IHC.c + age.c +
                                (1|TaskItem_num) + (1|LadlabID), 
                              family = "binomial", data = fig3.modelA.df)
fig3.modelA.main <- glmer(Accuracy ~ Productivity.tertiary + TaskItem_type +
                                IHC.c + age.c +
                                (1|TaskItem_num) + (1|LadlabID), 
                              family = "binomial", data = fig3.modelA.df)
fig3.modelA.full <- glmer(Accuracy ~ Productivity.tertiary + TaskItem_type +
                            Productivity.tertiary:TaskItem_type + IHC.c + age.c + 
                            (1|TaskItem_num) + (1|LadlabID), 
                          family = "binomial", data = fig3.modelA.df)

# LRT tests for productivity main effect
anova(fig3.modelA.main, fig3.modelA.itemtype, test='LRT')
# LRT test for itemtype main effect
anova(fig3.modelA.main, fig3.modelA.prod, test = 'LRT')
# LRT test for interaction effect
anova(fig3.modelA.full, fig3.modelA.main, test = 'LRT')
```

### Compare both productive groups

Build dataframe and mean-center IHC, FHC and age.
```{r, echo=FALSE}
fig3.modelB.df <- fig3.data %>%
  filter(Productivity.tertiary != "Nonproductive") %>%
  dplyr::select(c(LadlabID, IHC, FHC, Age, Productivity.tertiary,
                  TaskItem_num, TaskItem_type, Accuracy)) %>%
  mutate(Productivity.tertiary=as.factor(Productivity.tertiary),
         IHC = as.integer(IHC),
         LadlabID=as.factor(LadlabID),
         TaskItem_type=as.factor(TaskItem_type)) %>%
  mutate(IHC.c = as.vector(scale(IHC, center = TRUE, scale=TRUE)), #scale and center for model fit
         FHC.c = as.vector(scale(FHC, center = TRUE, scale=TRUE)), 
         age.c = as.vector(scale(Age, center = TRUE, scale=TRUE)))
str(fig3.modelB.df)
```

Regression testing for interaction of productivity and decade/non-decade item type on WCN accuracy
```{r}
##WCN model looking at interaction between productivity and decade/non-decade item accuracy
fig3.modelB.base <- glmer(Accuracy ~ age.c + 
                            (1|TaskItem_num) + (1|LadlabID),
                          family = "binomial", data = fig3.modelB.df)
fig3.modelB.ihc <- glmer(Accuracy ~ IHC.c + age.c + 
                           (1|TaskItem_num) + (1|LadlabID), 
                         family = "binomial", data = fig3.modelB.df)
fig3.modelB.prod <- glmer(Accuracy ~ Productivity.tertiary + IHC.c + age.c + 
                            (1|TaskItem_num) + (1|LadlabID), 
                          family = "binomial", data = fig3.modelB.df)
fig3.modelB.itemtype <- glmer(Accuracy ~ TaskItem_type +
                                IHC.c + age.c +
                                (1|TaskItem_num) + (1|LadlabID), 
                              family = "binomial", data = fig3.modelB.df)
fig3.modelB.main <- glmer(Accuracy ~ Productivity.tertiary + TaskItem_type +
                                IHC.c + age.c +
                                (1|TaskItem_num) + (1|LadlabID), 
                              family = "binomial", data = fig3.modelB.df)
fig3.modelB.full <- glmer(Accuracy ~ Productivity.tertiary + TaskItem_type +
                            Productivity.tertiary:TaskItem_type + IHC.c + age.c + 
                            (1|TaskItem_num) + (1|LadlabID), 
                          family = "binomial", data = fig3.modelB.df)

# LRT tests for productivity main effect
anova(fig3.modelB.main, fig3.modelB.itemtype, test='LRT')
# LRT test for itemtype main effect
anova(fig3.modelB.main, fig3.modelB.prod, test = 'LRT')
# LRT test for interaction effect
anova(fig3.modelB.full, fig3.modelB.main, test = 'LRT')

# summary of final model
summary(fig3.modelB.main)
```

### Analyses including all participants
```{r}
fig3.modelC.df <- fig3.data %>%
  dplyr::select(c(LadlabID, IHC, FHC, Age, Productivity,
                  TaskItem_num, TaskItem_type, Accuracy)) %>%
  mutate(Productivity=as.factor(Productivity),
         IHC = as.integer(IHC),
         LadlabID=as.factor(LadlabID),
         TaskItem_type=as.factor(TaskItem_type)) %>%
  mutate(IHC.c = as.vector(scale(IHC, center = TRUE, scale=TRUE)), #scale and center for model fit
         FHC.c = as.vector(scale(FHC, center = TRUE, scale=TRUE)), 
         age.c = as.vector(scale(Age, center = TRUE, scale=TRUE)))

## regressions
fig3.modelC.noint <- glmer(Accuracy ~ Productivity + TaskItem_type+ 
                             IHC.c + age.c + 
                             (1|TaskItem_num) + (1|LadlabID), 
                           family = "binomial", data = fig3.modelC.df)
# LRT tests
drop1(fig3.modelC.noint,test="Chisq")

# Test for interaction
fig3.modelC.full <- glmer(Accuracy ~ Productivity + TaskItem_type +
                            Productivity:TaskItem_type +
                         IHC.c + age.c + 
                             (1|TaskItem_num) + (1|LadlabID), 
                           family = "binomial", data = fig3.modelC.df)
anova(fig3.modelC.full, fig3.modelC.noint, test = 'LRT')
```



## Within / Outside IHC
Add whether the Task Item was within or outside of the kid's initial highest count.
```{r}
#first, get initial highest count for each kiddo
#Make a lookup table with SID and initial highest count
lookup <- full.data %>%
  distinct(LadlabID, IHC)

wcn.data %<>%
  dplyr::mutate(TaskItem = as.numeric(as.character(TaskItem)))

#This is a function that, for each trial, checks the number queried. If number queried is above the child's initial highest count, marks that trial as beyond count range.
determine_count_range <- function(df) {
  tmp <- df
  for (row in 1:nrow(tmp)) {
    sub = as.character(tmp[row, "LadlabID"])
    count_range = as.numeric(as.character(subset(lookup, LadlabID == sub)$IHC))
    tmp[row, "IHC"] = as.numeric(as.character(count_range))
    if (tmp[row, "TaskItem"] > count_range) {
      tmp[row, "WithinOutsideIHC"] = "outside"
    } else {
      tmp[row, "WithinOutsideIHC"] = "within"
    }
  }
  return(tmp)
}

#Run for wcn
wcn.data <- determine_count_range(wcn.data)
```

WCN accuracy, within and outside of IHC
```{r}
wcn.data %>%
  dplyr::filter(TaskType == "immediate") %>%
  dplyr::group_by(LadlabID, WithinOutsideIHC) %>%
  dplyr::summarize(score=mean(Accuracy, na.rm=T)) %>%
  ungroup() %>% group_by(WithinOutsideIHC) %>%
  dplyr::summarize(mean = mean(score, na.rm = TRUE), 
                   sd = sd(score, na.rm = TRUE))
```


Now WCN by within/outside count range and productivity
```{r}
wcn.data %>%
  dplyr::filter(TaskType == "immediate") %>%
  dplyr::group_by(LadlabID, Productivity, WithinOutsideIHC) %>%
  dplyr::summarize(score=mean(Accuracy, na.rm=T)) %>%
  ungroup() %>% group_by(Productivity, WithinOutsideIHC) %>%
  dplyr::summarize(mean = mean(score, na.rm = TRUE), 
                   sd = sd(score, na.rm = TRUE))

# three-way
wcn.data %>%
  dplyr::filter(TaskType == "immediate") %>%
  dplyr::group_by(LadlabID, Productivity.tertiary, WithinOutsideIHC) %>%
  dplyr::summarize(score=mean(Accuracy, na.rm=T)) %>%
  ungroup() %>% group_by(Productivity.tertiary, WithinOutsideIHC) %>%
  dplyr::summarize(mean = mean(score, na.rm = TRUE), 
                   sd = sd(score, na.rm = TRUE))
```


Plotting WCN as within vs. beyond by productivity 

```{r, echo=FALSE}
group_names <- c(`Productive` = "Productive Counters",
                    `Nonproductive` = "Nonproductive Counters")
# alternative 3, use fewer colors.
wcn.data %>%
  mutate(WithinOutsideIHC = factor(WithinOutsideIHC, levels = c("within", "outside"), 
                                   labels = c("Within IHC", "Beyond IHC")))%>%
  dplyr::filter(TaskType == "immediate") %>%
  dplyr::group_by(Productivity, WithinOutsideIHC, LadlabID, prod.gradient) %>%
  dplyr::summarize(meansubj = mean(Accuracy, na.rm = TRUE)) %>%
  ggplot(aes(x=WithinOutsideIHC, y=meansubj))+
  geom_violin(aes(color=Productivity), alpha=0.7, scale="count", position=position_dodge(width=0.8)) +
  geom_point(aes(fill=WithinOutsideIHC),
             position=position_jitterdodge(jitter.width=0.35,
                                           dodge.width=.9),
             alpha = .5) +
  stat_summary(aes(color=Productivity),
               fun.data = mean_cl_boot, geom="errorbar",
               position = position_dodge(width=0.8), width = 0.3)+
  stat_summary(aes(color=Productivity), fill="white",
               fun.y = mean,position = position_dodge(width=0.8), 
               geom="point", shape=33, size=3)+
  facet_grid(.~Productivity, labeller = as_labeller(group_names)) +
  scale_colour_manual(guide=FALSE, values=mypalette) + 
  scale_fill_brewer(guide=FALSE) +
  scale_y_continuous(limits=c(0,1)) +
  labs(y="Average Proportion Correct", x="Trial Type") +
  theme_bw(base_size = 13) +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank())

ggsave('graphs/wcn-within-beyond-violin.png', width=6, height=4)
```

Same graph but three-way productvity grouping
```{r, echo=FALSE}
# alternative 3, use fewer colors.
wcn.data %>%
  mutate(WithinOutsideIHC = factor(WithinOutsideIHC, levels = c("within", "outside"), 
                                   labels = c("Within IHC", "Beyond IHC")))%>%
  dplyr::filter(TaskType == "immediate") %>%
  dplyr::group_by(Productivity.tertiary, WithinOutsideIHC, LadlabID, prod.gradient) %>%
  dplyr::summarize(meansubj = mean(Accuracy, na.rm = TRUE)) %>%
  ggplot(aes(x=WithinOutsideIHC, y=meansubj))+
  geom_violin(aes(color=Productivity.tertiary), alpha=0.7, scale="count", position=position_dodge(width=0.8)) +
  geom_point(aes(fill=WithinOutsideIHC),
             position=position_jitterdodge(jitter.width=0.35,
                                           dodge.width=.9),
             alpha = .5) +
  stat_summary(aes(color=Productivity.tertiary),
               fun.data = mean_cl_boot, geom="errorbar",
               position = position_dodge(width=0.8), width = 0.3)+
  stat_summary(aes(color=Productivity.tertiary), fill="white",
               fun.y = mean,position = position_dodge(width=0.8), 
               geom="point", shape=33, size=3)+
  facet_grid(.~Productivity.tertiary, scales="free") +
  scale_colour_manual(guide=FALSE, values=mypalette) + 
  scale_fill_brewer(guide=FALSE) +
  scale_y_continuous(limits=c(0,1)) +
  labs(y="Average Proportion Correct", x="Trial Type") +
  theme_bw(base_size = 13) +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank())

ggsave('graphs/wcn-within-beyond-violinB.png', width=8, height=4)
```

### Fig 4
Try without violins
```{r}
## HM? 
wcn.data %>%
  mutate(WithinOutsideIHC = factor(WithinOutsideIHC, levels = c("within", "outside"), 
                                   labels = c("Within IHC", "Beyond IHC")))%>%
  dplyr::filter(TaskType == "immediate") %>%
  dplyr::group_by(Productivity.tertiary, WithinOutsideIHC, LadlabID, prod.gradient) %>%
  dplyr::summarize(meansubj = mean(Accuracy, na.rm = TRUE)) %>%
  ggplot(aes(x=WithinOutsideIHC, y=meansubj)) +
  stat_summary(aes(color=Productivity.tertiary),
               fun.data = mean_cl_boot, geom="errorbar",
               width = 0.3)+
  stat_summary(aes(color=Productivity.tertiary), fill="white",
               fun.y = mean,
#               position = position_dodge(width=0.8), 
               geom="point", shape=33, size=3) +
  stat_summary(fun.y="mean", geom="line", aes(color=Productivity.tertiary,
                                              group=factor(Productivity.tertiary))) +
      scale_colour_manual(values=prod.pal, name="Productivity") + 
  scale_fill_brewer(guide=FALSE) +
  scale_y_continuous(limits=c(0,1)) +
  labs(y="Average Proportion Correct", x="Trial Type") +
  theme_bw(base_size = 13) +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank())
ggsave('graphs/wcn-within-beyond-final.png', width=6, height=4)
```

### Analysis full sample

Analysis of WCN accuracy by productivity and trial type
```{r}
wcn_model.df <- wcn.data %>%
  filter(TaskType == "immediate")%>%
  mutate(IHC = as.integer(IHC),
         LadlabID = factor(LadlabID))%>%
  mutate(IHC.c = as.vector(scale(IHC, center = TRUE, scale=TRUE)), #scale and center for model fit
         age.c = as.vector(scale(Age, center = TRUE, scale=TRUE))) %>%
  dplyr::select(LadlabID, TaskItem_num, age.c, IHC.c, Productivity, WithinOutsideIHC, Accuracy)

##WCN model looking at interaction between productivity and trial type in WCN task
wcn.model.base <- glmer(Accuracy ~ age.c + (1|TaskItem_num) + (1|LadlabID), 
                        family = "binomial", data = wcn_model.df)
wcn.model.ihc <- glmer(Accuracy ~ IHC.c + age.c + (1|TaskItem_num) + (1|LadlabID), 
                       family = "binomial", data = wcn_model.df)
wcn.model.prod  <- glmer(Accuracy ~ Productivity +
                           IHC.c + age.c + (1|TaskItem_num) +
                     (1|LadlabID), family = "binomial", data = wcn_model.df)
wcn.model.withinout  <- glmer(Accuracy ~ WithinOutsideIHC +
                           IHC.c + age.c + (1|TaskItem_num) +
                     (1|LadlabID), family = "binomial", data = wcn_model.df)
wcn.model.noint <- glmer(Accuracy ~ Productivity + WithinOutsideIHC + 
                           IHC.c + age.c + (1|TaskItem_num) +
                     (1|LadlabID), family = "binomial", data = wcn_model.df)
wcn.model.int <- glmer(Accuracy ~ Productivity + WithinOutsideIHC + 
                         Productivity:WithinOutsideIHC + 
                         IHC.c + age.c + (1|TaskItem_num) +
                     (1|LadlabID), family = "binomial", data = wcn_model.df)

# compare against base models
anova(wcn.model.int, wcn.model.noint, wcn.model.ihc, wcn.model.base, test='LRT')

# test main effect productivity
anova(wcn.model.noint, wcn.model.withinout, test='LRT')
# test main effect within/outside
anova(wcn.model.noint, wcn.model.prod, test='LRT')
# test interaction 
anova(wcn.model.int, wcn.model.noint, test='LRT')
```


### Remove IHC=99
```{r, echo=FALSE}
wcn_model.df3 <- wcn.data %>%
  filter(TaskType == "immediate",
         Productivity.tertiary != "Productive (IHC \u3365 99)") %>%
  mutate(IHC = as.integer(IHC),
         LadlabID = factor(LadlabID))%>%
  mutate(IHC.c = as.vector(scale(IHC, center = TRUE, scale=TRUE)), #scale and center for model fit
         FHC.c = as.vector(scale(FHC, center = TRUE, scale=TRUE)), 
         age.c = as.vector(scale(Age, center = TRUE, scale=TRUE))) %>%
  dplyr::select(LadlabID, TaskItem_num, age.c, IHC.c, Productivity, WithinOutsideIHC, Accuracy)


##WCN model looking at interaction between productivity and trial type in WCN task
wcn.model3.base <- glmer(Accuracy ~ age.c + (1|TaskItem_num) + (1|LadlabID), 
                        family = "binomial", data = wcn_model.df3)
wcn.model3.ihc <- glmer(Accuracy ~ IHC.c + age.c + (1|TaskItem_num) + (1|LadlabID), 
                       family = "binomial", data = wcn_model.df3)
wcn.model3.noint <- glmer(Accuracy ~ Productivity + WithinOutsideIHC + 
                            IHC.c + age.c + (1|TaskItem_num) +
                     (1|LadlabID), family = "binomial", data = wcn_model.df3)
wcn.model3.prod  <- glmer(Accuracy ~ Productivity +
                           IHC.c + age.c + (1|TaskItem_num) +
                     (1|LadlabID), family = "binomial", data = wcn_model.df3)
wcn.model3.withinout  <- glmer(Accuracy ~ WithinOutsideIHC +
                           IHC.c + age.c + (1|TaskItem_num) +
                     (1|LadlabID), family = "binomial", data = wcn_model.df3)
wcn.model3.int <- glmer(Accuracy ~ Productivity+ WithinOutsideIHC + 
                         Productivity:WithinOutsideIHC + IHC.c + age.c + (1|TaskItem_num) +
                     (1|LadlabID), family = "binomial", data = wcn_model.df3)

#comparison against base models
anova(wcn.model3.int, wcn.model3.noint, wcn.model3.ihc, wcn.model3.base, test = 'LRT')

# test main effect productivity
anova(wcn.model3.noint, wcn.model3.withinout, test='LRT')
# test main effect within/outside
anova(wcn.model3.noint, wcn.model3.prod, test='LRT')
# test interaction 
anova(wcn.model3.int, wcn.model3.noint, test='LRT')

# summary of final model
summary(wcn.model3.int)
```

How many trials do kids have beyond their IHC?
```{r, echo=FALSE}
wcn.data %>%
  dplyr::filter(TaskType == "immediate") %>%
  dplyr::group_by(Productivity, WithinOutsideIHC)%>%
  dplyr::summarise(n = n())
```

# Infinity Descriptives

## Counts
Number of kids in each infinity category
```{r, echo=FALSE}
# Code the categories
full.data <- full.data %>% 
  mutate(Category = case_when(
    SuccessorKnower==0 & EndlessKnower==0 ~ "A Non-knower",
    SuccessorKnower==0 & EndlessKnower==1 ~ "B Endless-only",
    SuccessorKnower==1 & EndlessKnower==0 ~ "C Successor-only",
    SuccessorKnower==1 & EndlessKnower==1 ~ "D Full-knower"),
    InfinityKnower = factor(case_when(SuccessorKnower==0 | EndlessKnower==0 ~ 0,
                                      SuccessorKnower==1 & EndlessKnower==1 ~ 1),
                            levels=c(0,1)))

full.data %>%
  dplyr::distinct(LadlabID, Category, Productivity)%>%
  dplyr::group_by(Productivity, Category)%>%
  dplyr::summarise(n = n())
classification.data <- full.data %>%
  dplyr::distinct(LadlabID, EndlessKnower, SuccessorKnower, InfinityKnower,
                  Productivity, Productivity.tertiary)
# Cross tab
xtabs(~SuccessorKnower + EndlessKnower, classification.data)
```

Successor knowledge by productivity
```{r, echo=FALSE}
table(classification.data$SuccessorKnower, classification.data$Productivity)
chisq.test(table(classification.data$SuccessorKnower, classification.data$Productivity))
```

Endless knowledge by productivity
```{r, echo=FALSE}
#Endless contingency table
table(classification.data$EndlessKnower, classification.data$Productivity)
chisq.test(table(classification.data$EndlessKnower, classification.data$Productivity))
```

Infinity knowledge by productivity
```{r, echo=FALSE}
#Endless contingency table
table(classification.data$InfinityKnower, classification.data$Productivity)
chisq.test(table(classification.data$InfinityKnower, classification.data$Productivity))
```

## Age
Average age of kids for Endless and Successor Knowers
```{r, echo=FALSE}
full.data %>%
  dplyr::distinct(LadlabID, SuccessorKnower, Age)%>%
  dplyr::group_by(SuccessorKnower)%>%
  dplyr::summarise(meanAge = mean(Age),
                   sdAge = sd(Age),
                   meanAgeMonths = mean(Age)*13,
                   sdAgeMonths = sd(Age)*13) %>%
  kable(digits=3)

full.data %>%
  dplyr::distinct(LadlabID, EndlessKnower, Age)%>%
  dplyr::group_by(EndlessKnower)%>%
  dplyr::summarise(meanAge = mean(Age),
                   sdAge = sd(Age),
                   meanAgeMonths = mean(Age)*13,
                   sdAgeMonths = sd(Age)*13) %>%
  kable(digits=3)

full.data %>%
  dplyr::distinct(LadlabID, InfinityKnower, Age)%>%
  dplyr::group_by(InfinityKnower)%>%
  dplyr::summarise(meanAge = mean(Age),
                   sdAge = sd(Age),
                   meanAgeMonths = mean(Age)*13,
                   sdAgeMonths = sd(Age)*13) %>%
  kable(digits=3)
```

## HC
Infinity in relation to highest count
```{r, echo=FALSE}
full.data %>%
  dplyr::distinct(LadlabID, EndlessKnower, IHC, FHC) %>%
  dplyr::group_by(EndlessKnower) %>%
  dplyr::summarize(mean_IHC = mean(IHC),
                   mean_FHC = mean(FHC))

full.data %>%
  dplyr::distinct(LadlabID, SuccessorKnower, IHC, FHC) %>%
  dplyr::group_by(SuccessorKnower) %>%
  dplyr::summarize(mean_IHC = mean(IHC),
                   mean_FHC = mean(FHC))

full.data %>%
  dplyr::distinct(LadlabID, InfinityKnower, IHC, FHC) %>%
  dplyr::group_by(InfinityKnower) %>%
  dplyr::summarize(mean_IHC = mean(IHC),
                   mean_FHC = mean(FHC))
```

## WCN 
Infinity in relation to WCN
```{r, echo=FALSE}
full.data %>%
  dplyr::right_join(wcn.accuracy) %>%
  dplyr::distinct(LadlabID, EndlessKnower, wcnscore) %>%
  dplyr::group_by(EndlessKnower) %>%
  dplyr::summarize(mean_contig_nn = mean(wcnscore),
                   median_contig_nn = median(wcnscore))

full.data %>%
  dplyr::right_join(wcn.accuracy) %>%
  dplyr::distinct(LadlabID, SuccessorKnower, wcnscore) %>%
  dplyr::group_by(SuccessorKnower) %>%
  dplyr::summarize(mean_contig_nn = mean(wcnscore),
                   median_contig_nn = median(wcnscore))

full.data %>%
  dplyr::right_join(wcn.accuracy) %>%
  dplyr::distinct(LadlabID, InfinityKnower, wcnscore) %>%
  dplyr::group_by(InfinityKnower) %>%
  dplyr::summarize(mean_contig_nn = mean(wcnscore),
                   median_contig_nn = median(wcnscore))

```

# Productivity gradient

```{r, echo=FALSE}
ggplot(full.data, aes(x = IHC, y= prod.gradient, colour = Productivity.tertiary)) +
  geom_point(size = 3, alpha = .1)+
  geom_jitter()+
  theme_bw(base_size = 13) +
  theme(legend.position = "bottom") +
  scale_x_continuous(breaks = seq(0, 100, 10)) +
  scale_colour_manual(values = mypalette) + 
  labs(y = 'Productivity Gradient', x = 'IHC')
```

## Correlation between productivity gradient and IHC/FHC
```{r, echo=FALSE}
ms.cor <- full.data %>%
  distinct(LadlabID, Age, IHC, FHC, prod.gradient)

cor.test(ms.cor$IHC, ms.cor$prod.gradient) #sig. correlation between IHC and prod. gradient
cor.test(ms.cor$FHC, ms.cor$prod.gradient) #sig. correlation between FHC and prod. gradient
```

## Correlation between Productivity classification and Prod.gradient
```{r, echo=FALSE}
ms.cor <- full.data %>%
  dplyr::distinct(LadlabID, Productivity, prod.gradient)%>%
  mutate(Productivity = factor(Productivity, levels = c("Productive", "Nonproductive"),
                             labels = c(1, 0)), 
         Productivity = as.integer(as.character(Productivity)))

cor.test(ms.cor$Productivity, ms.cor$prod.gradient)
```


***

# Infinity Regression Analyses

## Setup
Counting, Productivity, and Infinity Battery
To identify whether there is connection between counting experience and Infinity Task performance, we will conduct three initial analyses, predicting Infinity Task performance from either (1) Initial Highest Count, (3) Productivity for Decade Rule (defined above), or (3) performance on the Next Number task. 

glm(inf.0/1 ~ (predictor) + age, family = binomial).

---
First, we need to make a model data frame that readily has all of this information

```{r}
#model base
# each participant only needs one row here, because we only need to know whether they are a Successor Knower or Endless Knower
model.df <- full.data %>%
  dplyr::distinct(LadlabID, Age, AgeGroup, Gender, 
                SuccessorKnower, EndlessKnower, InfinityKnower,
                IHC, Productivity, Productivity.tertiary, prod.gradient)
model.df <- right_join(model.df, wcn.accuracy, by="LadlabID") %>%
  mutate(SuccessorKnower = factor(SuccessorKnower, levels = c(0,1)), 
         EndlessKnower = factor(EndlessKnower, levels = c(0,1)),
         IHC = as.integer(IHC), 
         LadlabID = factor(LadlabID))
```

## Regression with All subjects
### prep
```{r}
#scale and center for model fit
distinct_model.df <- model.df %>%
  mutate(IHC.c = as.vector(scale(IHC, center = TRUE, scale=TRUE)), 
         Age.c = as.vector(scale(Age, center = TRUE, scale=TRUE)),
         prod.gradient.c = as.vector(scale(prod.gradient, center=TRUE, scale=TRUE)),
         wcnscore.c = as.vector(scale(wcnscore, center = TRUE, scale=TRUE)))

```
### Successor models
```{r}
###MODEL BUILDING AND COMPARISONS###
#base model for successor knower
base.successor <- glm(SuccessorKnower ~ Age.c, family = "binomial", 
                        data = distinct_model.df)

##IHC model##
model.ihc.successor <- glm(SuccessorKnower ~ IHC.c + Age.c, family = "binomial", 
                             data = distinct_model.df)
##WCN Model##
model.nn.successor <- glm(SuccessorKnower ~ wcnscore.c + Age.c, family = "binomial", 
                            data = distinct_model.df)
##Productivity model##
model.prod.successor <- glm(SuccessorKnower ~ Productivity + Age.c, family = "binomial",
                              data = distinct_model.df)

##EXPLORATORY## - GAIN SCORE
model.gain.successor <- glm(SuccessorKnower ~ prod.gradient.c + Age.c, family = "binomial",
                              data = distinct_model.df)

##Regression table for Successor Knower Models (Table )
mtable.sf.knowers <- mtable('Base' = base.successor,
            'IHC' = model.ihc.successor,
            'NN' = model.nn.successor,
            'Productivity' = model.prod.successor,
            'Prod. gain' = model.gain.successor,
            #summary.stats = c('R-squared','F','p','N'))
            summary.stats = c('Nagelkerke R-sq.','Log-likelihood','AIC','N'))
mtable.sf.knowers
write.mtable(mtable.sf.knowers, file="graphs/table3-all.txt")
```

#### Model comparisons

Comparing models with a single predictor against base model, we find that none of the predictors are significant in accounting for successor knowledge after controlling for age and IHC.
```{r}
#base v. IHC
anova(base.successor, model.ihc.successor, test = 'LRT') #IHC n.s.

#wcn v. base
anova(base.successor, model.nn.successor, test = 'LRT')#NN n.s.

#Productivity v. base
anova(base.successor, model.prod.successor, test = 'LRT')# n.s.

##Exploratory vs. base
anova(base.successor, model.gain.successor, test = 'LRT')# n.s.
```

### Endless models
```{r}
#Base model
base.endless <- glm(EndlessKnower ~ Age.c, family = "binomial", 
                      data = distinct_model.df)

###IHC MODEL###
model.ihc.endless <- glm(EndlessKnower ~ IHC.c + Age.c, family = "binomial", 
                           data = distinct_model.df)

### NN MODEL###
model.nn.endless <- glm(EndlessKnower ~ wcnscore.c + Age.c, family = "binomial", 
                          data = distinct_model.df) 

###PRODUCTIVITY MODEL###
model.prod.endless <- glm(EndlessKnower ~ Productivity + Age.c, family = "binomial", 
                            data = distinct_model.df)

##EXPLORATORY## - GAIN SCORE
model.gain.endless <- glm(EndlessKnower ~ prod.gradient.c + Age.c, family = "binomial", 
                          data = distinct_model.df)

##Regression table for Endless Models
mtable.endless.knowers <- mtable('Base' = base.endless,
            'IHC' = model.ihc.endless,
            'NN' = model.nn.endless,
            'Productivity' = model.prod.endless,
            'Prod. gradient' = model.gain.endless,
            summary.stats = c('Nagelkerke R-sq.','Log-likelihood','AIC','F','p','N'))

mtable.endless.knowers
write.mtable(mtable.endless.knowers, file="graphs/table3-all.txt")
```

#### Model comparisons
Unlike for successor knowledge, here we find that every predictor is significant addition to the base model.
```{r}
#base v. IHC
anova(base.endless, model.ihc.endless, test = 'LRT')

#base v. wcn accuracy
anova(model.nn.endless, base.endless, test = 'LRT')

#base v. productivity
anova(model.prod.endless, base.endless, test = 'LRT')

##Exploratory base v. productivity gradient
anova(base.endless, model.gain.endless, test = 'LRT')
```

### Full Infinity Knowledge models
```{r}
###MODEL BUILDING AND COMPARISONS###
#base model for successor knower
base.infinity <- glm(InfinityKnower ~ Age.c, family = "binomial", 
                        data = distinct_model.df)

##IHC model
model.ihc.infinity <- glm(InfinityKnower ~ IHC.c + Age.c, family = "binomial", 
                             data = distinct_model.df)
##Highest NN Model
model.nn.infinity <- glm(InfinityKnower ~ wcnscore.c + Age.c, family = "binomial", 
                            data = distinct_model.df)
##Productivity model
model.prod.infinity <- glm(InfinityKnower ~ Productivity + Age.c, family = "binomial",
                              data = distinct_model.df)

##Gain Score model
model.gain.infinity <- glm(InfinityKnower ~ prod.gradient.c + Age.c, family = "binomial",
                              data = distinct_model.df)

##Regression table for Infinity Knower Models (Table 4)
mtable.inf.knowers <- mtable('Base' = base.infinity,
            'IHC' = model.ihc.infinity,
            'NN' = model.nn.infinity,
            'Prod. Group' = model.prod.infinity,
            'Prod. Gain' = model.gain.infinity,
            #summary.stats = c('R-squared','F','p','N'))
            summary.stats = c('Nagelkerke R-sq.','Log-likelihood','AIC','N'))
mtable.inf.knowers
# save as txt
write.mtable(mtable.inf.knowers, file="graphs/table4-all.txt")
```

#### Model comparisons
```{r}
#base v. IHC
anova(base.infinity, model.ihc.infinity, test = 'LRT') #n.s.

#base v. highest contiguous
anova(base.infinity, model.nn.infinity, test = 'LRT')# significant.

#base v. productivity
anova(base.infinity, model.prod.infinity, test = 'LRT')#n.s. 

#base v. productivity gradient
anova(base.infinity, model.gain.infinity, test = 'LRT')#n.s.
```

### Visualizations
```{r, eval=FALSE}
large.successor.full.grad <- glm(SuccessorKnower ~ Productivity + wcnscore.c + 
                              IHC.c + Age.c, 
                            family = "binomial", data = distinct_model.df)
large.endless.full.grad <- glm(EndlessKnower ~ Productivity + wcnscore.c + 
                              IHC.c + Age.c, 
                            family = "binomial", data = distinct_model.df)
large.inf.full.grad <- glm(InfinityKnower ~ Productivity + wcnscore.c + 
                              IHC.c + Age.c, 
                            family = "binomial", data = distinct_model.df)

# maximal endless model
plot_model(large.endless.full.grad, type="std", transform="plogis",
           title="'Numbers do not end'",
           show.values = TRUE, colors="blue", value.offset = .3,
           axis.labels = c("Age.c"="Age", "wcnscore.c"="Next Number accuracy",
                           "IHC.c"= "Initial Highest Count",
                           "Productivity"="Productivity",
                           "Probabilities"="Endorsement Probability")) +
  ggplot3::geom_hline(yintercept = 0.5, linetype="dashed")
ggsave('graphs/regression-endless.png', width=6, height=3.5)

# maximal successor model
plot_model(large.successor.full.grad, type="std", transform="plogis",
           title="'Can always add one'",
           show.values = TRUE, colors="blue",value.offset = .3,
           axis.labels = c("Age.c"="Age", "wcnscore.c"="Next Number accuracy",
                           "IHC.c"= "Initial Highest Count",
                           "Productivity"="Productivity",
                           "Probabilities"="Endorsement Probability")) +
  ggplot3::geom_hline(yintercept = 0.5, linetype="dashed")
ggsave('graphs/regression-successor.png', width=6, height=3.5)

# maximal infinity model
plot_model(large.inf.full.grad, type="std", transform="plogis",
           title="Full infinity knowledge",
           show.values = TRUE, colors="blue",value.offset = .3,
           axis.labels = c("Age.c"="Age", "wcnscore.c"="Next Number accuracy",
                           "IHC.c"= "Initial Highest Count",
                           "Productivity"="Productivity",
                           "Probabilities"="Endorsement Probability")) +
  ggplot3::geom_hline(yintercept = 0.5, linetype="dashed")
ggsave('graphs/regression-fullinfinity.png', width=6, height=3.5)
```

## Correlations between variables
### LM predicting IHC from NN accuracy and age
```{r}
lm3 <- lm(IHC ~ wcnscore + Age.c, data = distinct_model.df)
summary(lm3)
```


## Regressions no ihc=99

### prep
```{r}
distinct_model.df3 <- model.df %>%
  filter(Productivity.tertiary != "Productive (IHC \u3365 99)") %>%
  mutate(IHC.c = as.vector(scale(IHC, center = TRUE, scale=TRUE)), #scale and center for model fit
         Age.c = as.vector(scale(Age, center = TRUE, scale=TRUE)),
         prod.gradient.c = as.vector(scale(prod.gradient, center=TRUE, scale=TRUE)),
        wcnscore.c = as.vector(scale(wcnscore, center = TRUE, scale=TRUE)))
```

### Successor models
```{r}
###MODEL BUILDING AND COMPARISONS###
#base model for successor knower
base.successor3 <- glm(SuccessorKnower ~ Age.c, family = "binomial", 
                        data = distinct_model.df3)

##IHC model##
model.ihc.successor3 <- glm(SuccessorKnower ~ IHC.c + Age.c, family = "binomial", 
                             data = distinct_model.df3)
##NN Model##
model.nn.successor3 <- glm(SuccessorKnower ~ wcnscore.c + Age.c, family = "binomial", 
                            data = distinct_model.df3)
##Productivity model##
model.prod.successor3 <- glm(SuccessorKnower ~ Productivity + Age.c, family = "binomial",
                              data = distinct_model.df3)

##EXPLORATORY## - GAIN SCORE
model.gain.successor3 <- glm(SuccessorKnower ~ prod.gradient.c + Age.c, family = "binomial",
                              data = distinct_model.df3)

##Regression table for Successor Knower Models (Table 3)
mtable.sf.knowers3 <- mtable('Base' = base.successor3,
            'IHC' = model.ihc.successor3,
            'NN' = model.nn.successor3,
            'Productivity' = model.prod.successor3,
            'Prod. gain' = model.gain.successor3,
            #summary.stats = c('R-squared','F','p','N'))
            summary.stats = c('Nagelkerke R-sq.','Log-likelihood','AIC','N'))
mtable.sf.knowers3
write.mtable(mtable.sf.knowers3, file="graphs/table3.txt")
```

#### Model comparisons
Looks like only IHC is a significant predictor. 
```{r}
#base v. IHC
anova(base.successor3, model.ihc.successor3, test = 'LRT') #IHC significant

#NN v. base
anova(base.successor3, model.nn.successor3, test = 'LRT')#NN not significant

#Productivity v. base
anova(base.successor3, model.prod.successor3, test = 'LRT')# n.s.

##Exploratory vs. base
anova(base.successor3, model.gain.successor3, test = 'LRT')# n.s.
```


### Endless Models
```{r}
#Base model
base.endless3 <- glm(EndlessKnower ~ Age.c, family = "binomial", 
                      data = distinct_model.df3)

###IHC MODEL###
model.ihc.endless3 <- glm(EndlessKnower ~ IHC.c + Age.c, family = "binomial", 
                           data = distinct_model.df3)

###WCN MODEL###
model.nn.endless3 <- glm(EndlessKnower ~ wcnscore.c + Age.c, family = "binomial", 
                          data = distinct_model.df3) 

###PRODUCTIVITY MODEL###
model.prod.endless3 <- glm(EndlessKnower ~ Productivity + Age.c, family = "binomial", 
                            data = distinct_model.df3)

##EXPLORATORY## - GAIN SCORE
model.gain.endless3 <- glm(EndlessKnower ~ prod.gradient.c + Age.c, family = "binomial", 
                          data = distinct_model.df3)

##Regression table for Endless Models
mtable.endless.knowers3 <- mtable('Base' = base.endless3,
            'IHC' = model.ihc.endless3,
            'NN' = model.nn.endless3,
            'Productivity' = model.prod.endless3,
            'Prod. gradient' = model.gain.endless3,
            summary.stats = c('Nagelkerke R-sq.','Log-likelihood','AIC','F','p','N'))

mtable.endless.knowers3
write.mtable(mtable.endless.knowers3, file="graphs/table3.txt")
```

#### Model comparisons
Only productivity (& productivity gain) is significant
```{r}
#base v. IHC
anova(base.endless3, model.ihc.endless3, test = 'LRT') #IHC not significant

#base v. highest contiguous
anova(model.nn.endless3, base.endless3, test = 'LRT')#not significant

#base v. productivity
anova(model.prod.endless3, base.endless3, test = 'LRT')#Prod significant

##Exploratory base v. productivity gradient
anova(base.endless3, model.gain.endless3, test = 'LRT')# prod. gradient significant
```


### Full Infinity Knowledge models
```{r}
###MODEL BUILDING AND COMPARISONS###
#base model for successor knower
base.infinity3 <- glm(InfinityKnower ~ Age.c, family = "binomial", 
                        data = distinct_model.df3)

##IHC model
model.ihc.infinity3 <- glm(InfinityKnower ~ IHC.c + Age.c, family = "binomial", 
                             data = distinct_model.df3)
##Highest NN Model
model.nn.infinity3 <- glm(InfinityKnower ~ wcnscore.c + Age.c, family = "binomial", 
                            data = distinct_model.df3)
##Productivity model
model.prod.infinity3 <- glm(InfinityKnower ~ Productivity + Age.c, family = "binomial",
                              data = distinct_model.df3)

##Gain Score model
model.gain.infinity3 <- glm(InfinityKnower ~ prod.gradient.c + Age.c, family = "binomial",
                              data = distinct_model.df3)

##Regression table for Infinity Knower Models (Table 4)
mtable.inf.knowers3 <- mtable('Base' = base.infinity3,
            'IHC' = model.ihc.infinity3,
            'NN' = model.nn.infinity3,
            'Prod. Group' = model.prod.infinity3,
            'Prod. Gain' = model.gain.infinity3,
            #summary.stats = c('R-squared','F','p','N'))
            summary.stats = c('Nagelkerke R-sq.','Log-likelihood','AIC','N'))
mtable.inf.knowers3
# save as txt
write.mtable(mtable.inf.knowers3, file="graphs/table4.txt")
```

#### Model comparisons
No variable is predictive. 
```{r}
#base v. IHC
anova(base.infinity3, model.ihc.infinity3, test = 'LRT') #n.s.

#base v. highest contiguous
anova(base.infinity3, model.nn.infinity3, test = 'LRT')# n.s.

#base v. productivity
anova(base.infinity3, model.prod.infinity3, test = 'LRT')#n.s. 

#base v. productivity gradient
anova(base.infinity3, model.gain.infinity3, test = 'LRT')#n.s.
```

### Visualizations
```{r, eval=FALSE}
large.endless.full3 <- glm(EndlessKnower ~ Productivity + wcnscore.c + 
                              IHC.c + Age.c, 
                            family = "binomial", data = distinct_model.df3)
large.successor.full3 <- glm(SuccessorKnower ~ Productivity + wcnscore.c + 
                              IHC.c + Age.c, 
                            family = "binomial", data = distinct_model.df3)
large.inf.full3 <- glm(InfinityKnower ~ Productivity + wcnscore.c + 
                              IHC.c + Age.c, 
                            family = "binomial", data = distinct_model.df3)

# maximal endless model
plot_model(large.endless.full3, type="std", transform="plogis",
           title="'Numbers do not end', exclude errorless kids",
           show.values = TRUE, colors="blue", value.offset = .3,
           axis.labels = c("Age.c"="Age", "wcnscore.c"="Next Number accuracy",
                           "IHC.c"= "Initial Highest Count",
                           "Productivity"="Productivity Status",
                           "Probabilities"="Endorsement Probability")) +
  ggplot3::geom_hline(yintercept = 0.5, linetype="dashed")
ggsave('graphs/regression-endless3.png', width=6, height=3.5)

# maximal successor model
plot_model(large.successor.full3, type="std", transform="plogis",
           title="'Can always add one', exclude errorless kids",
           show.values = TRUE, colors="blue",value.offset = .3,
           axis.labels = c("Age.c"="Age", "wcnscore.c"="Next Number accuracy",
                           "IHC.c"= "Initial Highest Count",
                           "Productivity"="Productivity Status",
                           "Probabilities"="Endorsement Probability")) +
  ggplot3::geom_hline(yintercept = 0.5, linetype="dashed")
ggsave('graphs/regression-successor3.png', width=6, height=3.5)

# maximal infinity model
plot_model(large.inf.full3, type="std", transform="plogis",
           title="Full infinity knowledge, exclude errorless kids",
           show.values = TRUE, colors="blue",value.offset = .3,
           axis.labels = c("Age.c"="Age", "wcnscore.c"="Next Number accuracy",
                           "IHC.c"= "Initial Highest Count",
                           "Productivity"="Productivity Status",
                           "Probabilities"="Endorsement Probability")) +
  ggplot3::geom_hline(yintercept = 0.5, linetype="dashed")
ggsave('graphs/regression-fullinfinity3.png', width=6, height=3.5)
```

## Regressions productive kids only

### prep
```{r}
distinct_model.df3 <- model.df %>%
  filter(Productivity.tertiary != "Nonproductive") %>%
  mutate(IHC.c = as.vector(scale(IHC, center = TRUE, scale=TRUE)), #scale and center for model fit
         Age.c = as.vector(scale(Age, center = TRUE, scale=TRUE)),
         prod.gradient.c = as.vector(scale(prod.gradient, center=TRUE, scale=TRUE)),
        wcnscore.c = as.vector(scale(wcnscore, center = TRUE, scale=TRUE)))
```

### Successor models
```{r}
###MODEL BUILDING AND COMPARISONS###
#base model for successor knower
base.successor3 <- glm(SuccessorKnower ~ Age.c, family = "binomial", 
                        data = distinct_model.df3)

##IHC model##
model.ihc.successor3 <- glm(SuccessorKnower ~ IHC.c + Age.c, family = "binomial", 
                             data = distinct_model.df3)
##NN Model##
model.nn.successor3 <- glm(SuccessorKnower ~ wcnscore.c + Age.c, family = "binomial", 
                            data = distinct_model.df3)
##Productivity model##
model.prod.successor3 <- glm(SuccessorKnower ~ Productivity.tertiary + Age.c, family = "binomial",
                              data = distinct_model.df3)

##EXPLORATORY## - GAIN SCORE
model.gain.successor3 <- glm(SuccessorKnower ~ prod.gradient.c + Age.c, family = "binomial",
                              data = distinct_model.df3)

##Regression table for Successor Knower Models (Table 3)
mtable.sf.knowers3 <- mtable('Base' = base.successor3,
            'IHC' = model.ihc.successor3,
            'NN' = model.nn.successor3,
            'Productivity' = model.prod.successor3,
            'Prod. gain' = model.gain.successor3,
            #summary.stats = c('R-squared','F','p','N'))
            summary.stats = c('Nagelkerke R-sq.','Log-likelihood','AIC','N'))
mtable.sf.knowers3
write.mtable(mtable.sf.knowers3, file="graphs/table2-prodonly.txt")
```

#### Model comparisons
Productivity gradient marginally significant, in negative direction.
```{r}
#base v. IHC
anova(base.successor3, model.ihc.successor3, test = 'LRT') #IHC significant

#NN v. base
anova(base.successor3, model.nn.successor3, test = 'LRT')#NN not significant

#Productivity v. base
anova(base.successor3, model.prod.successor3, test = 'LRT')# n.s.

##Exploratory vs. base
anova(base.successor3, model.gain.successor3, test = 'LRT')# n.s.
```


### Endless Models
```{r}
#Base model
base.endless3 <- glm(EndlessKnower ~ Age.c, family = "binomial", 
                      data = distinct_model.df3)

###IHC MODEL###
model.ihc.endless3 <- glm(EndlessKnower ~ IHC.c + Age.c, family = "binomial", 
                           data = distinct_model.df3)

###WCN MODEL###
model.nn.endless3 <- glm(EndlessKnower ~ wcnscore.c + Age.c, family = "binomial", 
                          data = distinct_model.df3) 

###PRODUCTIVITY MODEL###
model.prod.endless3 <- glm(EndlessKnower ~ Productivity.tertiary + Age.c, family = "binomial", 
                            data = distinct_model.df3)

##EXPLORATORY## - GAIN SCORE
model.gain.endless3 <- glm(EndlessKnower ~ prod.gradient.c + Age.c, family = "binomial", 
                          data = distinct_model.df3)

##Regression table for Endless Models
mtable.endless.knowers3 <- mtable('Base' = base.endless3,
            'IHC' = model.ihc.endless3,
            'NN' = model.nn.endless3,
            'Productivity' = model.prod.endless3,
            'Prod. gradient' = model.gain.endless3,
            summary.stats = c('Nagelkerke R-sq.','Log-likelihood','AIC','F','p','N'))

mtable.endless.knowers3
write.mtable(mtable.endless.knowers3, file="graphs/table3-prodonly.txt")
```

#### Model comparisons
WCN is significant.
```{r}
#base v. IHC
anova(base.endless3, model.ihc.endless3, test = 'LRT')

#base v. highest contiguous
anova(model.nn.endless3, base.endless3, test = 'LRT')

#base v. productivity
anova(model.prod.endless3, base.endless3, test = 'LRT')

##Exploratory base v. productivity gradient
anova(base.endless3, model.gain.endless3, test = 'LRT')
```


### Full Infinity Knowledge models
```{r}
###MODEL BUILDING AND COMPARISONS###
#base model for successor knower
base.infinity3 <- glm(InfinityKnower ~ Age.c, family = "binomial", 
                        data = distinct_model.df3)

##IHC model
model.ihc.infinity3 <- glm(InfinityKnower ~ IHC.c + Age.c, family = "binomial", 
                             data = distinct_model.df3)
##Highest NN Model
model.nn.infinity3 <- glm(InfinityKnower ~ wcnscore.c + Age.c, family = "binomial", 
                            data = distinct_model.df3)
##Productivity model
model.prod.infinity3 <- glm(InfinityKnower ~ Productivity.tertiary + Age.c, family = "binomial",
                              data = distinct_model.df3)

##Gain Score model
model.gain.infinity3 <- glm(InfinityKnower ~ prod.gradient.c + Age.c, family = "binomial",
                              data = distinct_model.df3)

##Regression table for Infinity Knower Models (Table 4)
mtable.inf.knowers3 <- mtable('Base' = base.infinity3,
            'IHC' = model.ihc.infinity3,
            'NN' = model.nn.infinity3,
            'Prod. Group' = model.prod.infinity3,
            'Prod. Gain' = model.gain.infinity3,
            #summary.stats = c('R-squared','F','p','N'))
            summary.stats = c('Nagelkerke R-sq.','Log-likelihood','AIC','N'))
mtable.inf.knowers3
# save as txt
write.mtable(mtable.inf.knowers3, file="graphs/table4-prodonly.txt")
```

#### Model comparisons
No variable is predictive. 
```{r}
#base v. IHC
anova(base.infinity3, model.ihc.infinity3, test = 'LRT') #n.s.

#base v. highest contiguous
anova(base.infinity3, model.nn.infinity3, test = 'LRT')# n.s.

#base v. productivity
anova(base.infinity3, model.prod.infinity3, test = 'LRT')#n.s. 

#base v. productivity gradient
anova(base.infinity3, model.gain.infinity3, test = 'LRT')#n.s.
```
